### 2024-03-02 paper/paper.tex
Basic code structure and paper files

\documentclass{article}
\usepackage{geometry}
\geometry{a4paper}

\title{Text-Mining Short Paper}
\author{Jianxin YU}
\date{2nd March 2024}

%%% BEGIN DOCUMENT
\begin{document}

\maketitle
% \tableofcontents

\section{Introduction}

\section{Method}

\end{document}

### 2024-03-02 models/__init__.py

@@ -1,0 +1,2 @@
+from .LSTM import LSTM
+from .LSTM_SP import LSTM_SP

### 2024-03-02 train.py

@@ -1,0 +1,38 @@
+import configs
+import models
+import numpy as np
+import os
+import time
+import datetime
+import json
+from sklearn.metrics import average_precision_score
+import sys
+import os
+import argparse
+# import IPython
+
+# sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument('--model_name', type = str, default = 'BiLSTM', help = 'name of the models')
+parser.add_argument('--save_name', type = str)
+
+parser.add_argument('--train_prefix', type = str, default = 'dev_train')
+parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
+
+
+args = parser.parse_args()
+model = {
+	'CNN3': models.CNN3,
+	'LSTM': models.LSTM,
+	'BiLSTM': models.BiLSTM,
+	'ContextAware': models.ContextAware,
+}
+
+con = config.Config(args)
+con.set_max_epoch(200)
+con.load_train_data()
+con.load_test_data()
+# con.set_train_model()
+con.train(model[args.model_name], args.save_name)

### 2024-03-02 train_sp.py

@@ -1,0 +1,40 @@
+import configs
+import models
+import numpy as np
+import os
+import time
+import datetime
+import json
+from sklearn.metrics import average_precision_score
+import sys
+import os
+import argparse
+# import IPython
+
+# sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument('--model_name', type = str, default = 'pcnn_att', help = 'name of the models')
+parser.add_argument('--save_name', type = str)
+
+parser.add_argument('--train_prefix', type = str, default = 'dev_train')
+parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
+parser.add_argument('--output_file', type = str, default = "result.json")
+
+
+args = parser.parse_args()
+model = {
+	# 'CNN3': models.CNN3,
+	# 'LSTM': models.LSTM,
+	# 'BiLSTM': models.BiLSTM,
+	# 'ContextAware': models.ContextAware,
+	'LSTM_SP': models.LSTM_SP
+}
+
+con = config.EviConfig(args)
+con.set_max_epoch(200)
+con.load_train_data()
+con.load_test_data()
+# con.set_train_model()
+con.train(model[args.model_name], args.save_name)

### 2024-03-02 configs/Config.py
fixed some issues of basic structure

@@ -44,7 +44,7 @@ class Config(object):
 		self.acc_NA = Accuracy()
 		self.acc_not_NA = Accuracy()
 		self.acc_total = Accuracy()
-		self.data_path = './prepro_data'
+		self.data_path = './data'
 		self.use_bag = False
 		self.use_gpu = True
 		self.is_training = True

### 2024-03-02 configs/__init__.py

@@ -1,1 +1,2 @@
 from .Config import Config
+from .EviConfig import EviConfig

### 2024-03-02 configs/gen_data.py

@@ -5,7 +5,7 @@ from nltk.tokenize import WordPunctTokenizer
 import argparse
 parser = argparse.ArgumentParser()
 parser.add_argument('--in_path', type = str, default =  "../data")
-parser.add_argument('--out_path', type = str, default = "prepro_data")
+parser.add_argument('--out_path', type = str, default = "../data")
 
 args = parser.parse_args()
 in_path = args.in_path

### 2024-03-02 train.py

@@ -13,26 +13,23 @@ import argparse
 
 # sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
 
+if __name__ == '__main__':
+	parser = argparse.ArgumentParser()
+	parser.add_argument('--model_name', type = str, default = 'LSTM', help = 'name of the models')
+	parser.add_argument('--save_name', type = str)
 
-parser = argparse.ArgumentParser()
-parser.add_argument('--model_name', type = str, default = 'BiLSTM', help = 'name of the models')
-parser.add_argument('--save_name', type = str)
-
-parser.add_argument('--train_prefix', type = str, default = 'dev_train')
-parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
+	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
+	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
 
 
-args = parser.parse_args()
-model = {
-	'CNN3': models.CNN3,
-	'LSTM': models.LSTM,
-	'BiLSTM': models.BiLSTM,
-	'ContextAware': models.ContextAware,
-}
+	args = parser.parse_args()
+	model = {
+		'LSTM': models.LSTM,
+	}
 
-con = config.Config(args)
-con.set_max_epoch(200)
-con.load_train_data()
-con.load_test_data()
-# con.set_train_model()
-con.train(model[args.model_name], args.save_name)
+	con = configs.Config(args)
+	con.set_max_epoch(200)
+	con.load_train_data()
+	con.load_test_data()
+	# con.set_train_model()
+	con.train(model[args.model_name], args.save_name)

### 2024-03-02 train_sp.py

@@ -32,7 +32,7 @@ model = {
 	'LSTM_SP': models.LSTM_SP
 }
 
-con = config.EviConfig(args)
+con = configs.EviConfig(args)
 con.set_max_epoch(200)
 con.load_train_data()
 con.load_test_data()

### 2024-03-02 train.py
fixed the model name

@@ -16,7 +16,7 @@ import argparse
 if __name__ == '__main__':
 	parser = argparse.ArgumentParser()
 	parser.add_argument('--model_name', type = str, default = 'LSTM', help = 'name of the models')
-	parser.add_argument('--save_name', type = str)
+	parser.add_argument('--save_name', type = str, default = 'LSTM')
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')

### 2024-03-02 configs/Config.py
add mps device for mac

@@ -94,6 +94,8 @@ class Config(object):
 		self.train_prefix = args.train_prefix
 		self.test_prefix = args.test_prefix
 
+		self.device = torch.device("mps" if self.use_gpu else "cpu")
+
 
 		if not os.path.exists("log"):
 			os.mkdir("log")
@@ -187,22 +189,22 @@ class Config(object):
 	def get_train_batch(self):
 		random.shuffle(self.train_order)
 
-		context_idxs = torch.LongTensor(self.batch_size, self.max_length).cuda()
-		context_pos = torch.LongTensor(self.batch_size, self.max_length).cuda()
-		h_mapping = torch.Tensor(self.batch_size, self.h_t_limit, self.max_length).cuda()
-		t_mapping = torch.Tensor(self.batch_size, self.h_t_limit, self.max_length).cuda()
-		relation_multi_label = torch.Tensor(self.batch_size, self.h_t_limit, self.relation_num).cuda()
-		relation_mask = torch.Tensor(self.batch_size, self.h_t_limit).cuda()
+		context_idxs = torch.LongTensor(self.batch_size, self.max_length).to(self.device)
+		context_pos = torch.LongTensor(self.batch_size, self.max_length).to(self.device)
+		h_mapping = torch.Tensor(self.batch_size, self.h_t_limit, self.max_length).to(self.device)
+		t_mapping = torch.Tensor(self.batch_size, self.h_t_limit, self.max_length).to(self.device)
+		relation_multi_label = torch.Tensor(self.batch_size, self.h_t_limit, self.relation_num).to(self.device)
+		relation_mask = torch.Tensor(self.batch_size, self.h_t_limit).to(self.device)
 
-		pos_idx = torch.LongTensor(self.batch_size, self.max_length).cuda()
+		pos_idx = torch.LongTensor(self.batch_size, self.max_length).to(self.device)
 
-		context_ner = torch.LongTensor(self.batch_size, self.max_length).cuda()
-		context_char_idxs = torch.LongTensor(self.batch_size, self.max_length, self.char_limit).cuda()
+		context_ner = torch.LongTensor(self.batch_size, self.max_length).to(self.device)
+		context_char_idxs = torch.LongTensor(self.batch_size, self.max_length, self.char_limit).to(self.device)
 
-		relation_label = torch.LongTensor(self.batch_size, self.h_t_limit).cuda()
[…]

### 2024-03-02 train.py
add CNN3 method

@@ -24,6 +24,7 @@ if __name__ == '__main__':
 
 	args = parser.parse_args()
 	model = {
+		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
 	}
 

### 2024-03-02 models/__init__.py
fixed issues of CNN

@@ -1,2 +1,3 @@
 from .LSTM import LSTM
 from .LSTM_SP import LSTM_SP
+from .CNN3 import CNN3

### 2024-03-02 train.py

@@ -29,7 +29,8 @@ if __name__ == '__main__':
 	}
 
 	con = configs.Config(args)
-	con.set_max_epoch(200)
+	con.set_max_epoch(10)
+	con.set_batch_size(24)
 	con.load_train_data()
 	con.load_test_data()
 	# con.set_train_model()

### 2024-03-02 models/__init__.py
add the BiAttention method

@@ -1,3 +1,5 @@
 from .LSTM import LSTM
+from .LSTM import BiAttention
 from .LSTM_SP import LSTM_SP
 from .CNN3 import CNN3
+from .Transformer import Transformer

### 2024-03-02 train.py

@@ -15,8 +15,8 @@ import argparse
 
 if __name__ == '__main__':
 	parser = argparse.ArgumentParser()
-	parser.add_argument('--model_name', type = str, default = 'LSTM', help = 'name of the models')
-	parser.add_argument('--save_name', type = str, default = 'LSTM')
+	parser.add_argument('--model_name', type = str, default = 'BiAttention', help = 'name of the models')
+	parser.add_argument('--save_name', type = str, default = 'BiAttention')
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
@@ -26,6 +26,7 @@ if __name__ == '__main__':
 	model = {
 		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
+		'BiAttention': models.BiAttention,
 	}
 
 	con = configs.Config(args)

### 2024-03-02 configs/Config.py
Add BERT method

@@ -727,8 +727,6 @@ class Config(object):
 
 		return f1, auc, pr_x, pr_y
 
-
-
 	def testall(self, model_pattern, model_name, input_theta):#, ignore_input_theta):
 		model = model_pattern(config = self)
 

### 2024-03-02 models/Transformer.py

@@ -1,0 +1,378 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.nn.utils.rnn as rnn
+
+from opt_einsum import contract
+
+
+class Transformer(nn.Module):
+    
+    def __init__(self, info, transformer):
+        super(Transformer, self).__init__()
+        
+        self.info = info
+        self.transformer = transformer
+        self.max_num_tokens = 512
+        
+        self.start_token_len, self.end_token_len = 1, 1
+        self.start_token_ids = torch.Tensor([transformer.config.cls_token_id]).to(info.DEVICE_GPU)
+        self.end_token_ids = torch.Tensor([transformer.config.sep_token_id]).to(info.DEVICE_GPU)
+        
+        
+    def forward(self, batch_token_seqs, batch_token_masks, batch_token_types):
+        
+        if 'roberta' in self.transformer.config._name_or_path: batch_token_types = torch.zeros_like(batch_token_types)
+
+        batch_size, batch_num_tokens = batch_token_seqs.size()
+        
+        if batch_num_tokens <= self.max_num_tokens:
+            batch_output = self.transformer(input_ids=batch_token_seqs, attention_mask=batch_token_masks, token_type_ids=batch_token_types, output_attentions=True)
+            batch_token_embs, batch_token_atts = batch_output[0], batch_output[-1][-1]
+            
+        else:
+            new_token_seqs, new_token_masks, new_token_types, new_token_segs = [], [], [], []
+            real_num_tokens = batch_token_masks.sum(1).int().tolist()
+            for doc_id, real_num_token in enumerate(real_num_tokens):
+                if real_num_token <= self.max_num_tokens:
+                    new_token_seqs.append(batch_token_seqs[doc_id, :self.max_num_tokens])
+                    new_token_masks.append(batch_token_masks[doc_id, :self.max_num_tokens])
+                    new_token_types.append(batch_token_types[doc_id, :self.max_num_tokens])
+                    new_token_segs.append(1)
+                else:
+                    new_token_seq1 = torch.cat([batch_token_seqs[doc_id, :self.max_num_tokens - self.end_token_len], self.end_token_ids], dim=-1)
+                    new_token_mask1 = batch_token_masks[doc_id, :self.max_num_tokens]
[…]

### 2024-03-02 models/__init__.py

@@ -2,4 +2,4 @@ from .LSTM import LSTM
 from .LSTM import BiAttention
 from .LSTM_SP import LSTM_SP
 from .CNN3 import CNN3
-from .Transformer import Transformer
+from .Transformer import BERT

### 2024-03-02 train.py

@@ -15,8 +15,8 @@ import argparse
 
 if __name__ == '__main__':
 	parser = argparse.ArgumentParser()
-	parser.add_argument('--model_name', type = str, default = 'BiAttention', help = 'name of the models')
-	parser.add_argument('--save_name', type = str, default = 'BiAttention')
+	parser.add_argument('--model_name', type = str, default = 'BERT', help = 'name of the models')
+	parser.add_argument('--save_name', type = str, default = 'BERT')
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
@@ -27,6 +27,7 @@ if __name__ == '__main__':
 		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
 		'BiAttention': models.BiAttention,
+		'BERT': models.BERT
 	}
 
 	con = configs.Config(args)

### 2024-03-02 train.py
set the TODOs for BERT method

@@ -26,8 +26,8 @@ if __name__ == '__main__':
 	model = {
 		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
-		'BiAttention': models.BiAttention,
-		'BERT': models.BERT
+		'BiAttention': models.BiAttention,  # TODO: Not work, may give up it
+		'BERT': models.BERT  # TODO: modify the info to config
 	}
 
 	con = configs.Config(args)

### 2024-03-02 models/__init__.py
add BiLSTM

@@ -1,5 +1,6 @@
 from .LSTM import LSTM
 from .LSTM import BiAttention
+from .BiLSTM import BiLSTM
 from .LSTM_SP import LSTM_SP
 from .CNN3 import CNN3
 from .Transformer import BERT

### 2024-03-02 train.py

@@ -26,6 +26,7 @@ if __name__ == '__main__':
 	model = {
 		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
+		'BiLSTM': models.BiLSTM,
 		'BiAttention': models.BiAttention,  # TODO: Not work, may give up it
 		'BERT': models.BERT  # TODO: modify the info to config
 	}

### 2024-03-02 SAIS/Code/info.py
add SAIS-BERT method independently

@@ -1,0 +1,86 @@
+import os
+import json
+
+
+class Info:
+    
+    def __init__(self, args):
+               
+        self.DEVICE_CPU = 'cpu'
+        self.DEVICE_GPU = 'mps'
+                
+        self.MARKER_ENTITY = '*'
+        self.EXTREME_SMALL_POSI = 1e-10
+        self.EXTREME_SMALL_NEGA = -1e10
+        
+        self.TASK_RE = 'RE'
+        self.TASK_CR = 'CR'
+        self.TASK_ET = 'ET'
+        self.TASK_PER = 'PER'
+        self.TASK_FER = 'FER'
+                
+        self.STAGE_PREPARE = 'Prepare'
+        self.STAGE_MAIN = 'Main'
+        
+        self.INFER_ROUND_FIRST = 'First'
+        self.INFER_ROUND_FER = 'FER'
+        self.INFER_ROUND_MASK = 'Mask'
+        self.INFER_ROUND_DOC = 'Doc'
+        self.INFER_ROUND_BLEND = 'Blend'
+        
+        self.DATASET = args.dataset        
+        self.DIR_CURR = os.getcwd()
+        self.DIR_DATA = os.path.join(self.DIR_CURR, '../Data')
+        self.DIR_DATASET = os.path.join(self.DIR_DATA, self.DATASET)
+        self.DIR_DATASET_ORI = os.path.join(self.DIR_DATASET, 'Original')
+        self.DIR_DATASET_PRO = os.path.join(self.DIR_DATASET, 'Processed')
+        self.DIR_DATASET_STD = os.path.join(self.DIR_DATASET, 'Stdout')
+
+        self.FILE_STDOUT = os.path.join(self.DIR_DATASET_STD, f'stdout_{args.stage}.txt')
+        self.FILE_MODEL = os.path.join(self.DIR_DATASET_PRO, f'model.pt')
+                            
+        if self.DATASET == 'DocRED':
+            self.load_DocRED()
+                    
+    
+    def load_DocRED(self):
+        
+        self.MODE_TRAIN = 'train_annotated'
+        self.MODE_DEV = 'dev'
+        self.MODE_TEST = 'test'
+        
[…]

### 2024-03-02 SAIS/Code/main.sh

@@ -1,0 +1,31 @@
+#!/bin/bash
+
+stage="Main"
+dataset="DocRED"
+seed=2021
+
+transformer="bert-base-cased" # "roberta-large"
+hidden_size=768
+bilinear_block_size=64
+
+RE_max=4
+CR_focal_gamma=2
+PER_focal_gamma=2
+FER_threshold=0.5
+
+loss_weight_CR=0.1
+loss_weight_ET=0.1
+loss_weight_PER=0.1
+loss_weight_FER=0.1
+
+num_epoch=20
+batch_size=1
+update_freq=1 
+
+new_lr=1e-4 
+pretrained_lr=5e-5
+warmup_ratio=0.06 
+max_grad_norm=1.0
+
+
+python3 main.py --stage=${stage} --dataset=${dataset} --seed=${seed} --transformer=${transformer} --hidden_size=${hidden_size} --bilinear_block_size=${bilinear_block_size} --RE_max=${RE_max} --CR_focal_gamma=${CR_focal_gamma} --PER_focal_gamma=${PER_focal_gamma} --FER_threshold=${FER_threshold} --loss_weight_CR=${loss_weight_CR} --loss_weight_ET=${loss_weight_ET} --loss_weight_PER=${loss_weight_PER} --loss_weight_FER=${loss_weight_FER} --num_epoch=${num_epoch} --batch_size=${batch_size} --update_freq=${update_freq} --new_lr=${new_lr} --pretrained_lr=${pretrained_lr} --warmup_ratio=${warmup_ratio} --max_grad_norm=${max_grad_norm}

### 2024-03-02 SAIS/Code/util.py

@@ -1,0 +1,405 @@
+import json
+import math
+import time
+import random
+import dill as pk
+import numpy as np
+from itertools import permutations
+from collections import defaultdict
+
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.nn.utils.rnn as rnn
+from transformers import AutoConfig, AutoModel, AutoTokenizer
+from transformers.optimization import AdamW, get_linear_schedule_with_warmup
+
+
+def set_seed(seed):
+    
+    random.seed(seed)
+    np.random.seed(seed)
+    torch.manual_seed(seed)
+    torch.cuda.manual_seed(seed)
+    torch.cuda.manual_seed_all(seed)
+
+    torch.backends.cudnn.enabled = False
+    torch.backends.cudnn.benchmark = False
+    torch.backends.cudnn.deterministic = True
+        
+        
+def myprint(text, file):
+    
+    file = open(file, 'a')
+    print(time.strftime("%Y %b %d %a, %H:%M:%S: ", time.localtime()) + text, file=file, flush=True)
+    file.close()
+    
+    
+def prepare_autos(args, info):
+    
+    config = AutoConfig.from_pretrained(args.transformer, num_labels=info.NUM_REL)
+    tokenizer = AutoTokenizer.from_pretrained(args.transformer)
+    transformer = AutoModel.from_pretrained(args.transformer, config=config)
+    
+    config.cls_token_id = tokenizer.cls_token_id
+    config.sep_token_id = tokenizer.sep_token_id
+    
+    return config, tokenizer, transformer
+
+
+def prepare_optimizer_scheduler(args, num_train_docs, model):
+    
+    grouped_parameters = defaultdict(list)
+    for name, param in model.named_parameters():
+        if 'transformer_module' in name: grouped_parameters['pretrained_lr'].append(param)
+        else: grouped_parameters['new_lr'].append(param)
+    grouped_lrs = [{'params':grouped_parameters[group], 'lr':lr} for group, lr in zip(['pretrained_lr', 'new_lr'], [args.pretrained_lr, args.new_lr])]
+    optimizer = AdamW(grouped_lrs)
+
+    num_updates = math.ceil(math.ceil(num_train_docs / args.batch_size) / args.update_freq) * args.num_epoch
+    num_warmups = int(num_updates * args.warmup_ratio)
[…]

### 2024-03-02 models/Transformer.py

@@ -1,378 +1,0 @@
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-import torch.nn.utils.rnn as rnn
-
-from opt_einsum import contract
-
-
-class Transformer(nn.Module):
-    
-    def __init__(self, info, transformer):
-        super(Transformer, self).__init__()
-        
-        self.info = info
-        self.transformer = transformer
-        self.max_num_tokens = 512
-        
-        self.start_token_len, self.end_token_len = 1, 1
-        self.start_token_ids = torch.Tensor([transformer.config.cls_token_id]).to(info.DEVICE_GPU)
-        self.end_token_ids = torch.Tensor([transformer.config.sep_token_id]).to(info.DEVICE_GPU)
-        
-        
-    def forward(self, batch_token_seqs, batch_token_masks, batch_token_types):
-        
-        if 'roberta' in self.transformer.config._name_or_path: batch_token_types = torch.zeros_like(batch_token_types)
-
-        batch_size, batch_num_tokens = batch_token_seqs.size()
-        
-        if batch_num_tokens <= self.max_num_tokens:
-            batch_output = self.transformer(input_ids=batch_token_seqs, attention_mask=batch_token_masks, token_type_ids=batch_token_types, output_attentions=True)
-            batch_token_embs, batch_token_atts = batch_output[0], batch_output[-1][-1]
-            
-        else:
-            new_token_seqs, new_token_masks, new_token_types, new_token_segs = [], [], [], []
-            real_num_tokens = batch_token_masks.sum(1).int().tolist()
-            for doc_id, real_num_token in enumerate(real_num_tokens):
-                if real_num_token <= self.max_num_tokens:
-                    new_token_seqs.append(batch_token_seqs[doc_id, :self.max_num_tokens])
-                    new_token_masks.append(batch_token_masks[doc_id, :self.max_num_tokens])
-                    new_token_types.append(batch_token_types[doc_id, :self.max_num_tokens])
-                    new_token_segs.append(1)
-                else:
-                    new_token_seq1 = torch.cat([batch_token_seqs[doc_id, :self.max_num_tokens - self.end_token_len], self.end_token_ids], dim=-1)
-                    new_token_mask1 = batch_token_masks[doc_id, :self.max_num_tokens]
[…]

### 2024-03-02 models/__init__.py

@@ -3,4 +3,3 @@ from .LSTM import BiAttention
 from .BiLSTM import BiLSTM
 from .LSTM_SP import LSTM_SP
 from .CNN3 import CNN3
-from .Transformer import BERT

### 2024-03-02 train.py

@@ -28,7 +28,6 @@ if __name__ == '__main__':
 		'LSTM': models.LSTM,
 		'BiLSTM': models.BiLSTM,
 		'BiAttention': models.BiAttention,  # TODO: Not work, may give up it
-		'BERT': models.BERT  # TODO: modify the info to config
 	}
 
 	con = configs.Config(args)

### 2024-03-04 models/LSTM.py
Add VAE layer and Attention layer on LSTM

@@ -12,234 +12,303 @@ from torch.nn.utils import rnn
 
 
 class LSTM(nn.Module):
-	def __init__(self, config):
-		super(LSTM, self).__init__()
-		self.config = config
+    def __init__(self, config):
+        super(LSTM, self).__init__()
+        self.config = config
 
-		word_vec_size = config.data_word_vec.shape[0]
-		self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
-		self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
-		self.word_emb.weight.requires_grad = False
+        word_vec_size = config.data_word_vec.shape[0]
+        self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
+        self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
+        self.word_emb.weight.requires_grad = False
 
-		# self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
-		# self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
-		# char_dim = config.data_char_vec.shape[1]
-		# char_hidden = 100
-		# self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
-		self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
-		self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
+        # self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
+        # self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
+        # char_dim = config.data_char_vec.shape[1]
+        # char_hidden = 100
+        # self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
+        self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
+        self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
 
-		input_size = config.data_word_vec.shape[1] + config.coref_size + config.entity_type_size #+ char_hidden
-		hidden_size = 128
+        input_size = config.data_word_vec.shape[1] + config.coref_size + config.entity_type_size #+ char_hidden
+        hidden_size = 128
 
-		# self.rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
[…]

### 2024-03-04 models/__init__.py

@@ -1,5 +1,2 @@
 from .LSTM import LSTM
-from .LSTM import BiAttention
-from .BiLSTM import BiLSTM
 from .LSTM_SP import LSTM_SP
-from .CNN3 import CNN3

### 2024-03-04 train.py

@@ -15,8 +15,8 @@ import argparse
 
 if __name__ == '__main__':
 	parser = argparse.ArgumentParser()
-	parser.add_argument('--model_name', type = str, default = 'BERT', help = 'name of the models')
-	parser.add_argument('--save_name', type = str, default = 'BERT')
+	parser.add_argument('--model_name', type = str, default = 'LSTM', help = 'name of the models')
+	parser.add_argument('--save_name', type = str, default = 'LSTM')
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
@@ -24,10 +24,7 @@ if __name__ == '__main__':
 
 	args = parser.parse_args()
 	model = {
-		'CNN3': models.CNN3,
 		'LSTM': models.LSTM,
-		'BiLSTM': models.BiLSTM,
-		'BiAttention': models.BiAttention,  # TODO: Not work, may give up it
 	}
 
 	con = configs.Config(args)

### 2024-03-06 SAIS/Code/info.py
Add the BERT method directory

@@ -1,86 +1,0 @@
-import os
-import json
-
-
-class Info:
-    
-    def __init__(self, args):
-               
-        self.DEVICE_CPU = 'cpu'
-        self.DEVICE_GPU = 'mps'
-                
-        self.MARKER_ENTITY = '*'
-        self.EXTREME_SMALL_POSI = 1e-10
-        self.EXTREME_SMALL_NEGA = -1e10
-        
-        self.TASK_RE = 'RE'
-        self.TASK_CR = 'CR'
-        self.TASK_ET = 'ET'
-        self.TASK_PER = 'PER'
-        self.TASK_FER = 'FER'
-                
-        self.STAGE_PREPARE = 'Prepare'
-        self.STAGE_MAIN = 'Main'
-        
-        self.INFER_ROUND_FIRST = 'First'
-        self.INFER_ROUND_FER = 'FER'
-        self.INFER_ROUND_MASK = 'Mask'
-        self.INFER_ROUND_DOC = 'Doc'
-        self.INFER_ROUND_BLEND = 'Blend'
-        
-        self.DATASET = args.dataset        
-        self.DIR_CURR = os.getcwd()
-        self.DIR_DATA = os.path.join(self.DIR_CURR, '../Data')
-        self.DIR_DATASET = os.path.join(self.DIR_DATA, self.DATASET)
-        self.DIR_DATASET_ORI = os.path.join(self.DIR_DATASET, 'Original')
-        self.DIR_DATASET_PRO = os.path.join(self.DIR_DATASET, 'Processed')
-        self.DIR_DATASET_STD = os.path.join(self.DIR_DATASET, 'Stdout')
-
-        self.FILE_STDOUT = os.path.join(self.DIR_DATASET_STD, f'stdout_{args.stage}.txt')
-        self.FILE_MODEL = os.path.join(self.DIR_DATASET_PRO, f'model.pt')
-                            
-        if self.DATASET == 'DocRED':
-            self.load_DocRED()
-                    
-    
-    def load_DocRED(self):
-        
-        self.MODE_TRAIN = 'train_annotated'
-        self.MODE_DEV = 'dev'
-        self.MODE_TEST = 'test'
-        
[…]

### 2024-03-06 SAIS/Code/main.py

@@ -1,350 +1,0 @@
-import json
-import math
-import argparse
-import dill as pk
-import numpy as np
-from collections import defaultdict
-
-import torch
-import torch.nn as nn
-import torch.optim as optim
-import torch.nn.functional as F
-from torch.nn.utils import clip_grad_norm_
-
-from info import Info
-from model import Model
-from prepare import DocInput
-from util import set_seed, myprint, prepare_autos, prepare_optimizer_scheduler, register_hyperparameters_main, cal_f1, evaluate, prepare_batch_train, prepare_batch_test, feed_batch
-
-
-def parse_args():
-    
-    parser = argparse.ArgumentParser()
-    
-    parser.add_argument('--stage', type=str, default='Main')
-    parser.add_argument('--dataset', type=str, default='DocRED')
-    parser.add_argument('--seed', type=int, default=66)
-    
-    parser.add_argument('--transformer', type=str, default='bert-base-cased')
-    parser.add_argument('--hidden_size', type=int, default=768)
-    parser.add_argument('--bilinear_block_size', type=int, default=64)
-        
-    parser.add_argument('--RE_max', type=int, default=4)
-    parser.add_argument('--CR_focal_gamma', type=int, default=2)
-    parser.add_argument('--PER_focal_gamma', type=int, default=2)
-    parser.add_argument('--FER_threshold', type=float, default=0.5)
-    
-    parser.add_argument('--loss_weight_CR', type=float, default=0.1)
-    parser.add_argument('--loss_weight_ET', type=float, default=0.1)
-    parser.add_argument('--loss_weight_PER', type=float, default=0.1)
-    parser.add_argument('--loss_weight_FER', type=float, default=0.1)
-    
-    parser.add_argument('--num_epoch', type=int, default=20)
-    parser.add_argument('--batch_size', type=int, default=4)
-    parser.add_argument('--update_freq', type=int, default=1)
-    
-    parser.add_argument('--new_lr', type=float, default=1e-4)
-    parser.add_argument('--pretrained_lr', type=float, default=5e-5)
-    parser.add_argument('--warmup_ratio', type=float, default=0.06)    
-    parser.add_argument('--max_grad_norm', type=float, default=1.0)
-    
-    args = parser.parse_args()
-    
-    return args
-
-
[…]

### 2024-03-06 SAIS/Code/main.sh

@@ -1,31 +1,0 @@
-#!/bin/bash
-
-stage="Main"
-dataset="DocRED"
-seed=2021
-
-transformer="bert-base-cased" # "roberta-large"
-hidden_size=768
-bilinear_block_size=64
-
-RE_max=4
-CR_focal_gamma=2
-PER_focal_gamma=2
-FER_threshold=0.5
-
-loss_weight_CR=0.1
-loss_weight_ET=0.1
-loss_weight_PER=0.1
-loss_weight_FER=0.1
-
-num_epoch=20
-batch_size=1
-update_freq=1 
-
-new_lr=1e-4 
-pretrained_lr=5e-5
-warmup_ratio=0.06 
-max_grad_norm=1.0
-
-
-python3 main.py --stage=${stage} --dataset=${dataset} --seed=${seed} --transformer=${transformer} --hidden_size=${hidden_size} --bilinear_block_size=${bilinear_block_size} --RE_max=${RE_max} --CR_focal_gamma=${CR_focal_gamma} --PER_focal_gamma=${PER_focal_gamma} --FER_threshold=${FER_threshold} --loss_weight_CR=${loss_weight_CR} --loss_weight_ET=${loss_weight_ET} --loss_weight_PER=${loss_weight_PER} --loss_weight_FER=${loss_weight_FER} --num_epoch=${num_epoch} --batch_size=${batch_size} --update_freq=${update_freq} --new_lr=${new_lr} --pretrained_lr=${pretrained_lr} --warmup_ratio=${warmup_ratio} --max_grad_norm=${max_grad_norm}

### 2024-03-06 SAIS/Code/prepare.py

@@ -1,162 +1,0 @@
-import json
-import argparse
-import dill as pk
-import numpy as np
-from collections import defaultdict
-
-import torch
-import torch.nn.utils.rnn as rnn
-
-from info import Info
-from util import myprint, prepare_autos, register_hyperparameters_prepare
-
-
-class DocInput:
-    
-    def __init__(self, title, doc_tokens, sid2tids, eid2tids, eid2etype, eids2rid2sids):
-        
-        self.title = title
-        self.doc_tokens = doc_tokens
-        self.sid2tids = sid2tids
-        
-        self.eid2tids = eid2tids
-        self.eid2etype = eid2etype
-        self.eids2rid2sids = eids2rid2sids
-
-
-def parse_args():
-    
-    parser = argparse.ArgumentParser()
-    parser.add_argument('--stage', type=str, default='Prepare')
-    parser.add_argument('--dataset', type=str, default='DocRED')
-    parser.add_argument('--transformer', type=str, default='bert-base-cased')
-    parser.add_argument('--max_seq_length', type=int, default=1024)
-
-    args = parser.parse_args()    
-    return args
-
-
-def type2vec(info, transformer, tokenizer, if_etype=False, if_rtype=False):
-        
-    if if_etype:
-        id2type, type2word = info.DATA_ID2NER, info.DATA_NER2WORD
-    elif if_rtype:
-        id2type, type2word = info.DATA_ID2REL, info.DATA_REL2WORD
-        
-    type_token_seqs, type_token_masks = [], []
-    for type_id in range(len(id2type)):
-        words = type2word.get(id2type[type_id], 'not applicable')
-        tokens = tokenizer.tokenize(words)
-        tokens = tokenizer.convert_tokens_to_ids(tokens)
-        type_token_seqs.append(torch.Tensor(tokens))
-        type_token_masks.append(torch.ones(len(tokens)))
-
-    type_token_seqs = rnn.pad_sequence(type_token_seqs, batch_first=True, padding_value=0).long()
-    type_token_masks = rnn.pad_sequence(type_token_masks, batch_first=True, padding_value=0).float()
-    type_embeddings = transformer(input_ids=type_token_seqs, attention_mask=type_token_masks)[0].detach()
-    type_embeddings[~type_token_masks.bool()] = info.EXTREME_SMALL_NEGA
[…]

### 2024-03-06 SAIS/Code/util.py

@@ -1,405 +1,0 @@
-import json
-import math
-import time
-import random
-import dill as pk
-import numpy as np
-from itertools import permutations
-from collections import defaultdict
-
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-import torch.nn.utils.rnn as rnn
-from transformers import AutoConfig, AutoModel, AutoTokenizer
-from transformers.optimization import AdamW, get_linear_schedule_with_warmup
-
-
-def set_seed(seed):
-    
-    random.seed(seed)
-    np.random.seed(seed)
-    torch.manual_seed(seed)
-    torch.cuda.manual_seed(seed)
-    torch.cuda.manual_seed_all(seed)
-
-    torch.backends.cudnn.enabled = False
-    torch.backends.cudnn.benchmark = False
-    torch.backends.cudnn.deterministic = True
-        
-        
-def myprint(text, file):
-    
-    file = open(file, 'a')
-    print(time.strftime("%Y %b %d %a, %H:%M:%S: ", time.localtime()) + text, file=file, flush=True)
-    file.close()
-    
-    
-def prepare_autos(args, info):
-    
-    config = AutoConfig.from_pretrained(args.transformer, num_labels=info.NUM_REL)
-    tokenizer = AutoTokenizer.from_pretrained(args.transformer)
-    transformer = AutoModel.from_pretrained(args.transformer, config=config)
-    
-    config.cls_token_id = tokenizer.cls_token_id
-    config.sep_token_id = tokenizer.sep_token_id
-    
-    return config, tokenizer, transformer
-
-
-def prepare_optimizer_scheduler(args, num_train_docs, model):
-    
-    grouped_parameters = defaultdict(list)
-    for name, param in model.named_parameters():
-        if 'transformer_module' in name: grouped_parameters['pretrained_lr'].append(param)
-        else: grouped_parameters['new_lr'].append(param)
-    grouped_lrs = [{'params':grouped_parameters[group], 'lr':lr} for group, lr in zip(['pretrained_lr', 'new_lr'], [args.pretrained_lr, args.new_lr])]
-    optimizer = AdamW(grouped_lrs)
-
-    num_updates = math.ceil(math.ceil(num_train_docs / args.batch_size) / args.update_freq) * args.num_epoch
-    num_warmups = int(num_updates * args.warmup_ratio)
[…]

### 2024-03-06 models/LSTM.py

@@ -52,9 +52,9 @@ class LSTM(nn.Module):
         # sent = torch.cat([self.word_emb(context_idxs), context_ch], dim=-1)
 
         context_mask = (context_idxs > 0).float()
-        context_output = self.vae(sent)
+        context_output = self.vae(sent)  # VAE to enhance the representation learning
         context_output = self.rnn(context_output, context_lens)
-        context_output = self.attention(context_output, context_output, context_mask)
+        context_output = self.attention(context_output, context_output, context_mask)  # Bi-attention
         context_output = torch.relu(self.linear_re(context_output))
 
         start_re_output = torch.matmul(h_mapping, context_output)

### 2024-03-06 configs/BERT_config.py
update BERT method

@@ -1,0 +1,115 @@
+#from pathlib import Path
+import torch
+from torch import nn
+
+#import pytorch_pretrained_bert as _bert
+from transformers import *
+
+import numpy as np
+
+#from dougu import flatten, lines
+
+
+
+class Bert():
+
+    MASK = '[MASK]'
+    CLS = "[CLS]"
+    SEP = "[SEP]"
+
+
+    def __init__(self, model_class, model_name):
+        super().__init__()
+        self.model_name = model_name
+        self.tokenizer = BertTokenizer.from_pretrained(self.model_name)
+        self.model = model_class.from_pretrained(model_name).to(torch.device("mps"))
+        self.max_len = self.model.embeddings.position_embeddings.weight.size(0)
+        self.dim = self.model.embeddings.position_embeddings.weight.size(1)
+
+    def tokenize(self, text, masked_idxs=None):
+        tokenized_text = self.tokenizer.tokenize(text)
+        if masked_idxs is not None:
+            for idx in masked_idxs:
+                tokenized_text[idx] = self.MASK
+        # prepend [CLS] and append [SEP]
+        # see https://github.com/huggingface/pytorch-pretrained-BERT/blob/master/examples/run_classifier.py#L195  # NOQA
+        tokenized = [self.CLS] + tokenized_text + [self.SEP]
+        return tokenized
+
+    def tokenize_to_ids(self, text, masked_idxs=None, pad=True):
+        tokens = self.tokenize(text, masked_idxs)
+        return self.convert_tokens_to_ids(tokens, pad=pad)
+
+    def convert_tokens_to_ids(self, tokens, pad=True):
+        token_ids = self.tokenizer.convert_tokens_to_ids(tokens)
+        ids = torch.tensor([token_ids])
+        assert ids.size(1) < self.max_len
+        if pad:
+            padded_ids = torch.zeros(1, self.max_len).to(ids)
+            padded_ids[0, :ids.size(1)] = ids
+            mask = torch.zeros(1, self.max_len).to(ids)
+            mask[0, :ids.size(1)] = 1
+            return padded_ids, mask
+        else:
+            return ids
+
+    def flatten(self, list_of_lists):
+        for list in list_of_lists:
+            for item in list:
+                yield item
+
+    def subword_tokenize(self, tokens):
+        """Segment each token into subwords while keeping track of
+        token boundaries.
+
+        Parameters
+        ----------
+        tokens: A sequence of strings, representing input tokens.
+
+        Returns
[…]

### 2024-03-06 configs/EviConfig.py

@@ -24,568 +24,568 @@ TRAIN_LIMIT = 3600
 test_evidence = False
 
 class Accuracy(object):
-	def __init__(self):
-		self.correct = 0
-		self.total = 0
-	def add(self, is_correct):
-		self.total += 1
-		if is_correct:
-			self.correct += 1
-	def get(self):
-		if self.total == 0:
-			return 0.0
-		else:
-			return float(self.correct) / self.total
-	def clear(self):
-		self.correct = 0
-		self.total = 0 
+    def __init__(self):
+        self.correct = 0
+        self.total = 0
+    def add(self, is_correct):
+        self.total += 1
+        if is_correct:
+            self.correct += 1
+    def get(self):
+        if self.total == 0:
+            return 0.0
+        else:
+            return float(self.correct) / self.total
+    def clear(self):
+        self.correct = 0
+        self.total = 0 
 
 class EviConfig(object):
-	def __init__(self, args):
-		self.acc_NA = Accuracy()
-		self.acc_not_NA = Accuracy()
-		self.acc_total = Accuracy()
-		self.data_path = './prepro_data'
-		self.use_bag = False
-		self.use_gpu = True
-		self.is_training = True
-		self.max_length = 512
-		self.pos_num = 2 * self.max_length
-		self.entity_num = self.max_length
-		self.relation_num = 97
-		self.coref_size = 20
-		self.entity_type_size = 20
-		self.max_epoch = 20
-		self.opt_method = 'Adam'
-		self.optimizer = None
-		self.drop_prob = 0.5 # for cnn
-		self.keep_prob = 0.8 # for lstm
-		self.checkpoint_dir = './checkpoint'
-		self.test_result_dir = './test_result'
-		self.test_epoch = 5
-		self.pretrain_model = None
-
-
-		self.word_size = 100
-		self.epoch_range = None
-		self.dropout = 0.5
-		self.period = 50
-
-		self.ins_batch_size = 40
-		self.test_ins_batch_size = self.ins_batch_size
-		self.batch_size = 4000
-
-
-		self.char_limit = 16
-		self.sent_limit = 25
-		self.dis2idx = np.zeros((512), dtype='int64')
-		self.dis2idx[1] = 1
-		self.dis2idx[2:] = 2
-		self.dis2idx[4:] = 3
-		self.dis2idx[8:] = 4
-		self.dis2idx[16:] = 5
[…]

### 2024-03-06 configs/gen_data.py

@@ -3,6 +3,11 @@ import os
 import json
 from nltk.tokenize import WordPunctTokenizer
 import argparse
+
+from tqdm import trange
+from transformers import *
+from BERT_config import Bert
+
 parser = argparse.ArgumentParser()
 parser.add_argument('--in_path', type = str, default =  "../data")
 parser.add_argument('--out_path', type = str, default = "../data")
@@ -13,6 +18,8 @@ out_path = args.out_path
 case_sensitive = False
 
 char_limit = 16
+sent_limit = 25
+word_size = 100
 train_distant_file_name = os.path.join(in_path, 'train_distant.json')
 train_annotated_file_name = os.path.join(in_path, 'train_annotated.json')
 dev_file_name = os.path.join(in_path, 'dev.json')
@@ -24,165 +31,187 @@ json.dump(id2rel, open(os.path.join(out_path, 'id2rel.json'), "w"))
 fact_in_train = set([])
 fact_in_dev_train = set([])
 
+bert = Bert(BertModel, 'bert-base-uncased')
+
+def sents_2_idx(sents, word2id):
+    #sents_idx = np.zeros([sent_limit, word_size]) + word2id['BLANK']
+    sents_idx = []
+    start_idx = 0
+    for i, sent in enumerate(sents[:sent_limit]):
+        sents_idx.append(list(range(start_idx, start_idx+len(sent))))
+        start_idx += len(sent)
+    return sents_idx
+
 def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix=''):
 
-	ori_data = json.load(open(data_file_name))
+    ori_data = json.load(open(data_file_name))
 
 
-	Ma = 0
-	Ma_e = 0
-	data = []
-	intrain = notintrain = notindevtrain = indevtrain = 0
-	for i in range(len(ori_data)):
-		Ls = [0]
-		L = 0
-		for x in ori_data[i]['sents']:
-			L += len(x)
-			Ls.append(L)
+    Ma = 0
+    Ma_e = 0
+    data = []
+    intrain = notintrain = notindevtrain = indevtrain = 0
+    word2id = json.load(open(os.path.join(out_path, "word2id.json")))
+    for i in range(len(ori_data)):
+        Ls = [0]
+        L = 0
+        for x in ori_data[i]['sents']:
+            L += len(x)
+            Ls.append(L)
 
-		vertexSet =  ori_data[i]['vertexSet']
-		# point position added with sent start position
-		for j in range(len(vertexSet)):
[…]

### 2024-03-06 models/BERT.py

@@ -1,0 +1,351 @@
+import torch
+import torch.autograd as autograd
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+from torch.autograd import Variable
+from torch import nn
+import numpy as np
+import math
+from torch.nn import init
+from models.attention import SimpleEncoder
+from torch.nn.utils import rnn
+from transformers import *
+from torch.nn.utils.rnn import pad_sequence
+
+
+class BERT(nn.Module):
+    def __init__(self, config):
+        super(BERT, self).__init__()
+        self.config = config
+
+        word_vec_size = config.data_word_vec.shape[0]
+        self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
+        self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
+
+        self.word_emb.weight.requires_grad = False
+        self.use_entity_type = True
+        self.use_coreference = True
+        self.use_distance = True
+
+        # performance is similar with char_embed
+        # self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
+        # self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
+
+        # char_dim = config.data_char_vec.shape[1]
+        # char_hidden = 100
+        # self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
+
+        hidden_size = 128
+        #hidden_size = 768
+        bert_hidden_size = 768
+        input_size = config.data_word_vec.shape[1]
+        if self.use_entity_type:
+            input_size += config.entity_type_size
+            self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
+
+        if self.use_coreference:
+            input_size += config.coref_size
+            # self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
+            self.entity_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
+
+        # input_size += char_hidden
+
+        self.input_size = input_size
+
+        #self.rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
+        #self.sent_rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
+        #self.att_enc = SimpleEncoder(input_size, 4, 1)
[…]

### 2024-03-06 models/__init__.py

@@ -1,2 +1,4 @@
 from .LSTM import LSTM
 from .LSTM_SP import LSTM_SP
+from .BERT import BERT
+from .ContextAware import ContextAware

### 2024-03-06 train.py

@@ -25,6 +25,8 @@ if __name__ == '__main__':
 	args = parser.parse_args()
 	model = {
 		'LSTM': models.LSTM,
+		'BERT': models.BERT,
+		'ContextAware': models.ContextAware,
 	}
 
 	con = configs.Config(args)

### 2024-03-06 train.py
set the pip requirements

@@ -15,8 +15,8 @@ import argparse
 
 if __name__ == '__main__':
 	parser = argparse.ArgumentParser()
-	parser.add_argument('--model_name', type = str, default = 'LSTM', help = 'name of the models')
-	parser.add_argument('--save_name', type = str, default = 'LSTM')
+	parser.add_argument('--model_name', type = str, default = 'BERT', help = 'name of the models')
+	parser.add_argument('--save_name', type = str, default = 'BERT')
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')

### 2024-03-06 configs/Config.py
modified config for BERT

@@ -10,7 +10,7 @@ import datetime
 import json
 import sys
 import sklearn.metrics
-from tqdm import tqdm
+from tqdm import tqdm, trange
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
@@ -23,714 +23,993 @@ IGNORE_INDEX = -100
 is_transformer = False
 
 class Accuracy(object):
-	def __init__(self):
-		self.correct = 0
-		self.total = 0
-	def add(self, is_correct):
-		self.total += 1
-		if is_correct:
-			self.correct += 1
-	def get(self):
-		if self.total == 0:
-			return 0.0
-		else:
-			return float(self.correct) / self.total
-	def clear(self):
-		self.correct = 0
-		self.total = 0 
+    def __init__(self):
+        self.correct = 0
+        self.total = 0
+    def add(self, is_correct):
+        self.total += 1
+        if is_correct:
+            self.correct += 1
+    def get(self):
+        if self.total == 0:
+            return 0.0
+        else:
+            return float(self.correct) / self.total
+    def clear(self):
+        self.correct = 0
+        self.total = 0
 
 class Config(object):
-	def __init__(self, args):
-		self.acc_NA = Accuracy()
-		self.acc_not_NA = Accuracy()
-		self.acc_total = Accuracy()
-		self.data_path = './data'
-		self.use_bag = False
-		self.use_gpu = True
-		self.is_training = True
-		self.max_length = 512
-		self.pos_num = 2 * self.max_length
-		self.entity_num = self.max_length
-		self.relation_num = 97
-
-		self.coref_size = 20
-		self.entity_type_size = 20
-		self.max_epoch = 20
-		self.opt_method = 'Adam'
-		self.optimizer = None
-
-		self.checkpoint_dir = './checkpoint'
-		self.fig_result_dir = './fig_result'
-		self.test_epoch = 5
-		self.pretrain_model = None
-
-
-		self.word_size = 100
-		self.epoch_range = None
-		self.cnn_drop_prob = 0.5  # for cnn
-		self.keep_prob = 0.8  # for lstm
-
-		self.period = 50
-
-		self.batch_size = 40
-		self.h_t_limit = 1800
-
-		self.test_batch_size = self.batch_size
-		self.test_relation_limit = 1800
-		self.char_limit = 16
-		self.sent_limit = 25
[…]

### 2024-03-06 configs/EviConfig.py
combine to main

@@ -1,591 +1,0 @@
-# coding: utf-8
-import torch
-import torch.nn as nn
-from torch.autograd import Variable
-import torch.optim as optim
-import numpy as np
-import os
-import time
-import datetime
-import json
-import sys
-import sklearn.metrics
-from tqdm import tqdm
-import matplotlib
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-import random
-from collections import defaultdict
-import torch.nn.functional as F
-
-
-IGNORE_INDEX = -100
-TRAIN_LIMIT = 3600
-test_evidence = False
-
-class Accuracy(object):
-    def __init__(self):
-        self.correct = 0
-        self.total = 0
-    def add(self, is_correct):
-        self.total += 1
-        if is_correct:
-            self.correct += 1
-    def get(self):
-        if self.total == 0:
-            return 0.0
-        else:
-            return float(self.correct) / self.total
-    def clear(self):
-        self.correct = 0
-        self.total = 0 
-
-class EviConfig(object):
-    def __init__(self, args):
-        self.acc_NA = Accuracy()
-        self.acc_not_NA = Accuracy()
-        self.acc_total = Accuracy()
-        self.data_path = './prepro_data'
-        self.use_bag = False
-        self.use_gpu = True
-        self.is_training = True
-        self.max_length = 512
-        self.pos_num = 2 * self.max_length
-        self.entity_num = self.max_length
-        self.relation_num = 97
-        self.coref_size = 20
-        self.entity_type_size = 20
-        self.max_epoch = 20
-        self.opt_method = 'Adam'
-        self.optimizer = None
-        self.drop_prob = 0.5 # for cnn
-        self.keep_prob = 0.8 # for lstm
-        self.checkpoint_dir = './checkpoint'
-        self.test_result_dir = './test_result'
-        self.test_epoch = 5
-        self.pretrain_model = None
-
-
-        self.word_size = 100
-        self.epoch_range = None
-        self.dropout = 0.5
-        self.period = 50
-
-        self.ins_batch_size = 40
-        self.test_ins_batch_size = self.ins_batch_size
-        self.batch_size = 4000
-
-
-        self.char_limit = 16
-        self.sent_limit = 25
-        self.dis2idx = np.zeros((512), dtype='int64')
-        self.dis2idx[1] = 1
-        self.dis2idx[2:] = 2
-        self.dis2idx[4:] = 3
-        self.dis2idx[8:] = 4
-        self.dis2idx[16:] = 5
[…]

### 2024-03-06 configs/__init__.py

@@ -1,2 +1,3 @@
 from .Config import Config
 from .EviConfig import EviConfig
+from .gen_data import generate_data

### 2024-03-06 configs/gen_data.py

@@ -9,8 +9,8 @@ from transformers import *
 from BERT_config import Bert
 
 parser = argparse.ArgumentParser()
-parser.add_argument('--in_path', type = str, default =  "../data")
-parser.add_argument('--out_path', type = str, default = "../data")
+parser.add_argument('--in_path', type = str, default =  "./data")
+parser.add_argument('--out_path', type = str, default = "./data")
 
 args = parser.parse_args()
 in_path = args.in_path
@@ -214,10 +214,10 @@ def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix=''
     print("Finish saving")
 
 
-
-init(train_distant_file_name, rel2id, max_length = 512, is_training = True, suffix='')
-init(train_annotated_file_name, rel2id, max_length = 512, is_training = False, suffix='_train')
-init(dev_file_name, rel2id, max_length = 512, is_training = False, suffix='_dev')
-init(test_file_name, rel2id, max_length = 512, is_training = False, suffix='_test')
+def generate_data():
+    init(train_distant_file_name, rel2id, max_length = 512, is_training = True, suffix='')
+    init(train_annotated_file_name, rel2id, max_length = 512, is_training = False, suffix='_train')
+    init(dev_file_name, rel2id, max_length = 512, is_training = False, suffix='_dev')
+    init(test_file_name, rel2id, max_length = 512, is_training = False, suffix='_test')
 
 

### 2024-03-06 evaluation.py

@@ -29,133 +29,135 @@ def gen_train_facts(data_file_name, truth_dir):
 
     return fact_in_train
 
-input_dir = sys.argv[1]
-output_dir = sys.argv[2]
 
-submit_dir = os.path.join(input_dir, 'res')
-truth_dir = os.path.join(input_dir, 'ref')
+def evaluate():
+    input_dir = sys.argv[1]
+    output_dir = sys.argv[2]
 
-if not os.path.isdir(submit_dir):
-    print ("%s doesn't exist" % submit_dir)
+    submit_dir = os.path.join(input_dir, 'res')
+    truth_dir = os.path.join(input_dir, 'ref')
 
-if os.path.isdir(submit_dir) and os.path.isdir(truth_dir):
-    if not os.path.exists(output_dir):
-        os.makedirs(output_dir)
+    if not os.path.isdir(submit_dir):
+        print ("%s doesn't exist" % submit_dir)
 
-    fact_in_train_annotated = gen_train_facts("../data/train_annotated.json", truth_dir)
-    fact_in_train_distant = gen_train_facts("../data/train_distant.json", truth_dir)
+    if os.path.isdir(submit_dir) and os.path.isdir(truth_dir):
+        if not os.path.exists(output_dir):
+            os.makedirs(output_dir)
 
-    output_filename = os.path.join(output_dir, 'scores.txt')
-    output_file = open(output_filename, 'w')
+        fact_in_train_annotated = gen_train_facts("./data/train_annotated.json", truth_dir)
+        fact_in_train_distant = gen_train_facts("./data/train_distant.json", truth_dir)
 
-    truth_file = os.path.join(truth_dir, "dev_test.json")
-    truth = json.load(open(truth_file))
+        output_filename = os.path.join(output_dir, 'scores.txt')
+        output_file = open(output_filename, 'w')
 
-    std = {}
-    tot_evidences = 0
-    titleset = set([])
+        truth_file = os.path.join(truth_dir, "dev_test.json")
+        truth = json.load(open(truth_file))
 
-    title2vectexSet = {}
+        std = {}
+        tot_evidences = 0
+        titleset = set([])
 
-    for x in truth:
-        title = x['title']
-        titleset.add(title)
+        title2vectexSet = {}
 
-        vertexSet = x['vertexSet']
-        title2vectexSet[title] = vertexSet
+        for x in truth:
+            title = x['title']
+            titleset.add(title)
 
-        for label in x['labels']:
-            r = label['r']
[…]

### 2024-03-06 main.py

@@ -1,0 +1,16 @@
+from configs import generate_data
+from evaluation import evaluate
+from train import train
+
+
+def main():
+    generate_data()
+    # model_name = 'BERT' or 'LSTM'
+    # device = 'mps', 'cuda' or 'cpu'
+    train('BERT', 'mps')
+
+    evaluate()
+
+
+if __name__ == '__main__':
+    main()

### 2024-03-06 train.py

@@ -1,3 +1,5 @@
+import torch
+
 import configs
 import models
 import numpy as np
@@ -13,10 +15,11 @@ import argparse
 
 # sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
 
-if __name__ == '__main__':
+
+def train(model_name='BERT', device='mps'):
 	parser = argparse.ArgumentParser()
-	parser.add_argument('--model_name', type = str, default = 'BERT', help = 'name of the models')
-	parser.add_argument('--save_name', type = str, default = 'BERT')
+	parser.add_argument('--model_name', type = str, default = model_name, help = 'name of the models')
+	parser.add_argument('--save_name', type = str, default = model_name)
 
 	parser.add_argument('--train_prefix', type = str, default = 'dev_train')
 	parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
@@ -30,6 +33,7 @@ if __name__ == '__main__':
 	}
 
 	con = configs.Config(args)
+	con.device = torch.device(device)
 	con.set_max_epoch(10)
 	con.set_batch_size(24)
 	con.load_train_data()

### 2024-03-06 train_sp.py

@@ -1,40 +1,0 @@
-import configs
-import models
-import numpy as np
-import os
-import time
-import datetime
-import json
-from sklearn.metrics import average_precision_score
-import sys
-import os
-import argparse
-# import IPython
-
-# sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
-
-
-parser = argparse.ArgumentParser()
-parser.add_argument('--model_name', type = str, default = 'pcnn_att', help = 'name of the models')
-parser.add_argument('--save_name', type = str)
-
-parser.add_argument('--train_prefix', type = str, default = 'dev_train')
-parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
-parser.add_argument('--output_file', type = str, default = "result.json")
-
-
-args = parser.parse_args()
-model = {
-	# 'CNN3': models.CNN3,
-	# 'LSTM': models.LSTM,
-	# 'BiLSTM': models.BiLSTM,
-	# 'ContextAware': models.ContextAware,
-	'LSTM_SP': models.LSTM_SP
-}
-
-con = configs.EviConfig(args)
-con.set_max_epoch(200)
-con.load_train_data()
-con.load_test_data()
-# con.set_train_model()
-con.train(model[args.model_name], args.save_name)

### 2024-03-06 main.py
combine to main

@@ -4,11 +4,14 @@ from train import train
 
 
 def main():
-    generate_data()
+    # if you want to generate data, run this line
+    # generate_data()
+
     # model_name = 'BERT' or 'LSTM'
     # device = 'mps', 'cuda' or 'cpu'
     train('BERT', 'mps')
 
+    # if you want to evaluate the model, run this line
     evaluate()
 
 

### 2024-03-06 configs/BERT_config.py
modified some issues

@@ -18,11 +18,11 @@ class Bert():
     SEP = "[SEP]"
 
 
-    def __init__(self, model_class, model_name):
+    def __init__(self, model_class, model_name, device='mps'):
         super().__init__()
         self.model_name = model_name
         self.tokenizer = BertTokenizer.from_pretrained(self.model_name)
-        self.model = model_class.from_pretrained(model_name).to(torch.device("mps"))
+        self.model = model_class.from_pretrained(model_name).to(torch.device(device))
         self.max_len = self.model.embeddings.position_embeddings.weight.size(0)
         self.dim = self.model.embeddings.position_embeddings.weight.size(1)
 

### 2024-03-06 configs/__init__.py

@@ -1,3 +1,3 @@
 from .Config import Config
-from .EviConfig import EviConfig
 from .gen_data import generate_data
+from .BERT_config import Bert

### 2024-03-06 configs/gen_data.py

@@ -6,7 +6,7 @@ import argparse
 
 from tqdm import trange
 from transformers import *
-from BERT_config import Bert
+from configs.BERT_config import Bert
 
 parser = argparse.ArgumentParser()
 parser.add_argument('--in_path', type = str, default =  "./data")
@@ -31,8 +31,6 @@ json.dump(id2rel, open(os.path.join(out_path, 'id2rel.json'), "w"))
 fact_in_train = set([])
 fact_in_dev_train = set([])
 
-bert = Bert(BertModel, 'bert-base-uncased')
-
 def sents_2_idx(sents, word2id):
     #sents_idx = np.zeros([sent_limit, word_size]) + word2id['BLANK']
     sents_idx = []
@@ -42,7 +40,8 @@ def sents_2_idx(sents, word2id):
         start_idx += len(sent)
     return sents_idx
 
-def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix=''):
+def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix='', device='mps'):
+    bert = Bert(BertModel, 'bert-base-uncased', device=device)
 
     ori_data = json.load(open(data_file_name))
 
@@ -214,10 +213,10 @@ def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix=''
     print("Finish saving")
 
 
-def generate_data():
-    init(train_distant_file_name, rel2id, max_length = 512, is_training = True, suffix='')
-    init(train_annotated_file_name, rel2id, max_length = 512, is_training = False, suffix='_train')
-    init(dev_file_name, rel2id, max_length = 512, is_training = False, suffix='_dev')
-    init(test_file_name, rel2id, max_length = 512, is_training = False, suffix='_test')
+def generate_data(device='mps'):
+    init(train_distant_file_name, rel2id, max_length = 512, is_training = True, suffix='', device=device)
+    init(train_annotated_file_name, rel2id, max_length = 512, is_training = False, suffix='_train', device=device)
+    init(dev_file_name, rel2id, max_length = 512, is_training = False, suffix='_dev', device=device)
+    init(test_file_name, rel2id, max_length = 512, is_training = False, suffix='_test', device=device)
 
 

### 2024-03-06 main.py

@@ -5,7 +5,7 @@ from train import train
 
 def main():
     # if you want to generate data, run this line
-    # generate_data()
+    #generate_data(device='mps')
 
     # model_name = 'BERT' or 'LSTM'
     # device = 'mps', 'cuda' or 'cpu'

### 2024-03-07 configs/Config.py
add test

@@ -865,18 +865,18 @@ class Config(object):
 
 
 
-    def testall(self, model_pattern, model_name, input_theta, two_phase=False, pretrain_model_name=None):#, ignore_input_theta):
+    def testall(self, model_pattern, model_name, input_theta, two_phase=False, pretrain_model_name=None):#, ignore_input_theta
         pretrain_model = None
         if two_phase:
             pretrain_model = model_pattern(config = self)
             pretrain_model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, pretrain_model_name)))
-            pretrain_model.cuda()
+            pretrain_model.to(self.device)
             pretrain_model.eval()
 
         model = model_pattern(config = self)
 
         model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, model_name)))
-        model.cuda()
+        model.to(self.device)
         model.eval()
         #self.test_anylyse(model, model_name, True, input_theta)
         f1, auc, pr_x, pr_y = self.test(model, model_name, True, input_theta, two_phase, pretrain_model)

### 2024-03-07 evaluation.py

@@ -1,163 +1,0 @@
-#!/usr/bin/env python
-import sys
-import os
-import os.path
-import json
-
-def gen_train_facts(data_file_name, truth_dir):
-    fact_file_name = data_file_name[data_file_name.find("train_"):]
-    fact_file_name = os.path.join(truth_dir, fact_file_name.replace(".json", ".fact"))
-
-    if os.path.exists(fact_file_name):
-        fact_in_train = set([])
-        triples = json.load(open(fact_file_name))
-        for x in triples:
-            fact_in_train.add(tuple(x))
-        return fact_in_train
-
-    fact_in_train = set([])
-    ori_data = json.load(open(data_file_name))
-    for data in ori_data:
-        vertexSet = data['vertexSet']
-        for label in data['labels']:
-            rel = label['r']
-            for n1 in vertexSet[label['h']]:
-                for n2 in vertexSet[label['t']]:
-                    fact_in_train.add((n1['name'], n2['name'], rel))
-
-    json.dump(list(fact_in_train), open(fact_file_name, "w"))
-
-    return fact_in_train
-
-
-def evaluate():
-    input_dir = sys.argv[1]
-    output_dir = sys.argv[2]
-
-    submit_dir = os.path.join(input_dir, 'res')
-    truth_dir = os.path.join(input_dir, 'ref')
-
-    if not os.path.isdir(submit_dir):
-        print ("%s doesn't exist" % submit_dir)
-
-    if os.path.isdir(submit_dir) and os.path.isdir(truth_dir):
-        if not os.path.exists(output_dir):
-            os.makedirs(output_dir)
-
-        fact_in_train_annotated = gen_train_facts("./data/train_annotated.json", truth_dir)
-        fact_in_train_distant = gen_train_facts("./data/train_distant.json", truth_dir)
-
-        output_filename = os.path.join(output_dir, 'scores.txt')
-        output_file = open(output_filename, 'w')
-
-        truth_file = os.path.join(truth_dir, "dev_test.json")
-        truth = json.load(open(truth_file))
-
-        std = {}
-        tot_evidences = 0
-        titleset = set([])
-
-        title2vectexSet = {}
-
-        for x in truth:
-            title = x['title']
-            titleset.add(title)
-
-            vertexSet = x['vertexSet']
-            title2vectexSet[title] = vertexSet
-
-            for label in x['labels']:
-                r = label['r']
-
-                h_idx = label['h']
[…]

### 2024-03-07 main.py

@@ -1,5 +1,5 @@
 from configs import generate_data
-from evaluation import evaluate
+from test.test import test
 from train import train
 
 
@@ -12,7 +12,7 @@ def main():
     train('BERT', 'mps')
 
     # if you want to evaluate the model, run this line
-    evaluate()
+    test('BERT', 'mps')
 
 
 if __name__ == '__main__':

### 2024-03-07 test/test.py

@@ -1,0 +1,43 @@
+import configs
+import models
+import numpy as np
+import os
+import time
+import datetime
+import json
+from sklearn.metrics import average_precision_score
+import sys
+import os
+import argparse
+import torch
+# import IPython
+
+# sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
+
+
+def test(model_name='BERT', device='mps'):
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--model_name', type = str, default = model_name, help = 'name of the model')
+    parser.add_argument('--save_name', type = str)
+
+    parser.add_argument('--train_prefix', type = str, default = 'train')
+    parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
+    parser.add_argument('--input_theta', type = float, default = -1)
+    parser.add_argument('--two_phase', action='store_true')
+    # parser.add_argument('--ignore_input_theta', type = float, default = -1)
+
+
+    args = parser.parse_args()
+    model = {
+        'LSTM': models.LSTM,
+        'BERT': models.BERT,
+        'ContextAware': models.ContextAware,
+    }
+
+    con = configs.Config(args)
+    con.device = torch.device(device)
+    #con.load_train_data()
+    con.load_test_data()
+    # con.set_train_model()
+    pretrain_model_name = 'checkpoint_' + model_name + '_bert_relation_exist_cls'
+    con.testall(model[args.model_name], args.save_name, args.input_theta, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)

### 2024-03-07 paper/paper.tex
fixed some issues of basic structure
fixed issues of CNN
add the readme and predict module

@@
-\documentclass{article}
-\usepackage{geometry}
-\geometry{a4paper}
+% Preamble
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+
+% Packages
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{hyperref}
+
+\def\BibTeX{{
+        \rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX
+    }
+}
 
 \title{Text-Mining Short Paper}
-\author{Jianxin YU}
-\date{2nd March 2024}
+\author{
+    \IEEEauthorblockN{
+        Qixuan Yang
+    }
+    \IEEEauthorblockA{
+        \textit{
+            Computer Science
+        } \\
+        \textit{
+            University of Manchester
+        }\\
+        Manchester, the United Kingdom \\
+        qixuan.yang@postgrad.manchester.ac.uk
+    }
+    \and
+    \IEEEauthorblockN{
+        Hong Wang
+    }
+    \IEEEauthorblockA{
+        \textit{
+            Computer Science
+        } \\
+        \textit{
+            University of Manchester
+        }\\
+        Manchester, the United Kingdom \\
+        hong.wang-5@student.manchester.ac.uk
+    }
+    \and
+    \IEEEauthorblockN{
+        Matei-Alexandru Costin
+    }
+    \IEEEauthorblockA{
+        \textit{
+            Computer Science
+        } \\
+        \textit{
+            University of Manchester
+        }\\
+        Manchester, the United Kingdom \\
+        matei-alexandru.costin@student.manchester.ac.uk
+    }
+    \and
+    \IEEEauthorblockN{
+        Jianxin Yu
+    }
+    \IEEEauthorblockA{
+        \textit{
+            Computer Science
+        } \\
+        \textit{
+            University of Manchester
+        }\\
+        Manchester, the United Kingdom \\
+        jianxin.yu@postgrad.manchester.ac.uk
+    }
+}
 
@@
 \begin{document}
+\maketitle
 
-\maketitle
-% \tableofcontents
+\begin{abstract}
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+\end{abstract}
+
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
+
+% Requirements:
+% The paper content should be at most four pages long, plus any number of pages for references and any appendices.
 
 \section{Introduction}
+% (1) provide an introduction to the RE task and describe your chosen RE dataset;
 
-\section{Method}
+DocRed dataset\cite{yao2019docred}
+
+\section{Literature Review}
+% (2) review previously reported work that is related to your approaches;
+
+DocRed dataset with LSTM\cite{yao2019docred}
+
+CNN\cite{yao2019docred}
+
+BiLSTM\cite{yao2019docred}
+
+SAIS-BERT\cite{xiao2021sais}
+
+GAIN-BERT\cite{zeng2020double}
+
+Two-steps BERT\cite{wang2019fine}
+
+DREEAM\cite{ma2023dreeam}
+
+SSAN-RoBERTa-large+Adaptation\cite{xu2021entity}
+
+KD-Rb-l\cite{tan2022document}
+
+\section{Approaches}
+% (3) describe the two RE approaches that you developed, justifying why they were chosen and detailing how they were implemented;
+
+Two RE approaches: LSTM\cite{yao2019docred} updated with VAE layer and attention layer, and BERT\cite{zeng2020double} updated with ...
+
+\section{Evaluation}
+% (4) describe how you evaluated the approaches (e.g., using which metrics); 
+% here we should find out the popular evaluations in previous papers, such as precision, accuracy or F1 score. 
+Previous papers all use F1 score to evaluate the methods work on relation extraction (RE).
+
+\section{Results}
+% (5) discuss the results of your evaluation, comparing the approaches and highlighting their strengths and weaknesses.
+
+\bibliography{references}
+\bibliographystyle{unsrt}
 

### 2024-03-07 configs/Config.py

@@ -77,6 +77,7 @@ class Config(object):
         self.h_t_limit = 1800
 
         self.test_batch_size = self.batch_size
+        self.predict_batch_size = self.batch_size
         self.test_relation_limit = 1800
         self.char_limit = 16
         self.sent_limit = 25
@@ -194,6 +195,40 @@ class Config(object):
 
         self.test_order = list(range(self.test_len))
         self.test_order.sort(key=lambda x: np.sum(self.data_test_word[x] > 0), reverse=True)
+
+    def load_predict_data(self):
+        print("Reading testing data...")
+        self.data_word_vec = np.load(os.path.join(self.data_path, 'vec.npy'))
+        self.data_char_vec = np.load(os.path.join(self.data_path, 'char_vec.npy'))
+        self.rel2id = json.load(open(os.path.join(self.data_path, 'rel2id.json')))
+        self.id2rel = {v: k for k,v in self.rel2id.items()}
+
+        prefix = self.test_prefix
+        print (prefix)
+        self.is_predict = ('dev_test_predict' == prefix)
+        self.data_predict_word = np.load(os.path.join(self.data_path, prefix+'_word.npy'))
+        self.data_predict_pos = np.load(os.path.join(self.data_path, prefix+'_pos.npy'))
+        self.data_predict_ner = np.load(os.path.join(self.data_path, prefix+'_ner.npy'))
+        self.data_predict_char = np.load(os.path.join(self.data_path, prefix+'_char.npy'))
+        self.predict_file = json.load(open(os.path.join(self.data_path, prefix+'.json')))
+
+        self.data_predict_bert_word = np.load(os.path.join(self.data_path, prefix+'_bert_word.npy'))
+        self.data_predict_bert_mask = np.load(os.path.join(self.data_path, prefix+'_bert_mask.npy'))
+        self.data_predict_bert_starts = np.load(os.path.join(self.data_path, prefix+'_bert_starts.npy'))
+
+
+        self.predict_len = self.data_predict_word.shape[0]
+        assert(self.predict_len==len(self.predict_file))
+
+
+        print("Finish reading")
+
+        self.predict_batches = self.data_predict_word.shape[0] // self.predict_batch_size
+        if self.data_predict_word.shape[0] % self.predict_batch_size != 0:
+            self.predict_batches += 1
+
+        self.predict_order = list(range(self.predict_len))
+        self.predict_order.sort(key=lambda x: np.sum(self.data_predict_word[x] > 0), reverse=True)
 
[…]

### 2024-03-07 configs/__init__.py

@@ -1,3 +1,3 @@
 from .Config import Config
-from .gen_data import generate_data
+from .gen_data import generate_data, generate_test_predict
 from .BERT_config import Bert

### 2024-03-07 configs/gen_data.py

@@ -24,6 +24,7 @@ train_distant_file_name = os.path.join(in_path, 'train_distant.json')
 train_annotated_file_name = os.path.join(in_path, 'train_annotated.json')
 dev_file_name = os.path.join(in_path, 'dev.json')
 test_file_name = os.path.join(in_path, 'test.json')
+test_predict_file_name = os.path.join(in_path, 'test_predict.json')
 
 rel2id = json.load(open(os.path.join(out_path, 'rel2id.json'), "r"))
 id2rel = {v:u for u,v in rel2id.items()}
@@ -219,4 +220,7 @@ def generate_data(device='mps'):
     init(dev_file_name, rel2id, max_length = 512, is_training = False, suffix='_dev', device=device)
     init(test_file_name, rel2id, max_length = 512, is_training = False, suffix='_test', device=device)
 
+
+def generate_test_predict(device='mps'):
+    init(test_predict_file_name, rel2id, max_length = 512, is_training = False, suffix='_test_predict', device=device)
 

### 2024-03-07 main.py

@@ -1,18 +1,62 @@
+import argparse
+import json
+
+from nltk import word_tokenize, PorterStemmer
+from nltk.corpus import stopwords
+
 from configs import generate_data
+from configs import generate_test_predict
 from test.test import test
+from test.test_predict import predict
 from train import train
 
 
+def tokenize_data(text, output_file):
+    words = word_tokenize(text)
+
+    # 去除停用词
+    stop_words = set(stopwords.words('english'))
+    words = [word for word in words if word not in stop_words]
+
+    # 词干提取
+    ps = PorterStemmer()
+    words = [ps.stem(word) for word in words]
+
+    with open(output_file, 'w') as f:
+        json.dump(words, f)
+
+
+def data_preprocess(text, device='mps'):
+    # tokenize data
+    tokenize_data(text, '.data/test_predict.json')
+
+    # generate data
+    generate_test_predict(device='mps')
+
+
 def main():
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--run_type', type=str, default='predict')
+    parser.add_argument('--model_name', type=str, default='LSTM')
+    parser.add_argument('--need_generate_data', type=bool, default=False)
+    parser.add_argument('--device', type=str, default='mps')
+
+    args = parser.parse_args()
     # if you want to generate data, run this line
-    #generate_data(device='mps')
+    if args.need_generate_data:
+        generate_data(device=args.device)
 
     # model_name = 'BERT' or 'LSTM'
     # device = 'mps', 'cuda' or 'cpu'
-    train('BERT', 'mps')
-
-    # if you want to evaluate the model, run this line
-    test('BERT', 'mps')
+    if args.run_type == 'train':
+        train(args.model_name, args.device)
+    elif args.run_type == 'test':
+        # if you want to predict, run this line
+        test(args.model_name, args.device)
+    elif args.run_type == 'predict':
+        text = input('Please input the text you want to predict: ')
+        data_preprocess(text, args.device)
+        predict(args.model_name, args.device)
 
 
 if __name__ == '__main__':

### 2024-03-07 test/test_predict.py

@@ -1,0 +1,43 @@
+import configs
+import models
+import numpy as np
+import os
+import time
+import datetime
+import json
+from sklearn.metrics import average_precision_score
+import sys
+import os
+import argparse
+import torch
+# import IPython
+
+# sys.excepthook = IPython.core.ultratb.FormattedTB(mode='Verbose', color_scheme='Linux', call_pdb=1)
+
+
+def predict(model_name='BERT', device='mps'):
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--model_name', type = str, default = model_name, help = 'name of the model')
+    parser.add_argument('--save_name', type = str)
+
+    parser.add_argument('--train_prefix', type = str, default = 'train')
+    parser.add_argument('--test_prefix', type = str, default = 'dev_test_predict')
+    parser.add_argument('--input_theta', type = float, default = -1)
+    parser.add_argument('--two_phase', action='store_true')
+    # parser.add_argument('--ignore_input_theta', type = float, default = -1)
+
+
+    args = parser.parse_args()
+    model = {
+        'LSTM': models.LSTM,
+        'BERT': models.BERT,
+        'ContextAware': models.ContextAware,
+    }
+
+    con = configs.Config(args)
+    con.device = torch.device(device)
+    #con.load_train_data()
+    con.load_predict_data()
+    # con.set_train_model()
+    pretrain_model_name = 'checkpoint_' + model_name + '_bert_relation_exist_cls'
+    con.test_predect(model[args.model_name], args.save_name, args.input_theta, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)

### 2024-03-07 train.py
update the readme

@@ -34,7 +34,7 @@ def train(model_name='BERT', device='mps'):
 
 	con = configs.Config(args)
 	con.device = torch.device(device)
-	con.set_max_epoch(10)
+	con.set_max_epoch(100)
 	con.set_batch_size(24)
 	con.load_train_data()
 	con.load_test_data()

### 2024-03-07 configs/Config.py
fixed some issues

@@ -79,6 +79,7 @@ class Config(object):
         self.test_batch_size = self.batch_size
         self.predict_batch_size = self.batch_size
         self.test_relation_limit = 1800
+        self.predict_relation_limit = 1800
         self.char_limit = 16
         self.sent_limit = 25
         #self.combined_sent_limit = 200
@@ -877,8 +878,11 @@ class Config(object):
                     is_rel_exist = pretrain_model(context_idxs, context_pos, context_ner, context_char_idxs, input_lengths,
                                    h_mapping, t_mapping, relation_mask, dis_h_2_t, dis_t_2_h, sent_idxs, sent_lengths, reverse_sent_idxs, context_masks, context_starts)
 
-                predict_re = model(context_idxs, context_pos, context_ner, context_char_idxs, input_lengths,
+                if model_name == 'BERT':
+                    predict_re = model(context_idxs, context_pos, context_ner, context_char_idxs, input_lengths,
                                    h_mapping, t_mapping, relation_mask, dis_h_2_t, dis_t_2_h, sent_idxs, sent_lengths, reverse_sent_idxs, context_masks, context_starts)
+                else:
+                    predict_re = model(context_idxs, context_pos, context_ner, context_char_idxs, input_lengths, h_mapping, t_mapping, relation_mask, dis_h_2_t, dis_t_2_h)
 
                 predict_re = torch.sigmoid(predict_re)
 
@@ -1035,13 +1039,13 @@ class Config(object):
         pretrain_model = None
         if two_phase:
             pretrain_model = model_pattern(config = self)
-            pretrain_model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, pretrain_model_name)))
+            pretrain_model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, pretrain_model_name), map_location=self.device))
             pretrain_model.to(self.device)
             pretrain_model.eval()
 
         model = model_pattern(config = self)
 
-        model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, model_name)))
+        model.load_state_dict(torch.load(os.path.join(self.checkpoint_dir, model_name), map_location=self.device))
         model.to(self.device)
         model.eval()
         #self.test_anylyse(model, model_name, True, input_theta)
@@ -1052,13 +1056,13 @@ class Config(object):
         pretrain_model = None
         if two_phase:
             pretrain_model = model_pattern(config=self)
[…]

### 2024-03-07 configs/gen_data.py

@@ -59,7 +59,7 @@ def init(data_file_name, rel2id, max_length = 512, is_training = True, suffix=''
             L += len(x)
             Ls.append(L)
 
-        vertexSet =  ori_data[i]['vertexSet']
+        vertexSet = ori_data[i]['vertexSet']
         # point position added with sent start position
         for j in range(len(vertexSet)):
             for k in range(len(vertexSet[j])):

### 2024-03-07 main.py

@@ -1,37 +1,84 @@
 import argparse
 import json
 
-from nltk import word_tokenize, PorterStemmer
+from nltk import word_tokenize, PorterStemmer, download, pos_tag
 from nltk.corpus import stopwords
 
 from configs import generate_data
 from configs import generate_test_predict
-from test.test import test
-from test.test_predict import predict
+from test import test, predict
 from train import train
 
 
-def tokenize_data(text, output_file):
+def tokenize_data(text, title, output_file):
+    download('punkt')
+    download('stopwords')
+    download('averaged_perceptron_tagger')  # download the tagger
+
+    # Load ner2id.json
+    with open('./data/ner2id.json', 'r') as f:
+        ner2id = json.load(f)
+
     words = word_tokenize(text)
 
-    # 去除停用词
     stop_words = set(stopwords.words('english'))
     words = [word for word in words if word not in stop_words]
 
-    # 词干提取
     ps = PorterStemmer()
     words = [ps.stem(word) for word in words]
 
-    with open(output_file, 'w') as f:
-        json.dump(words, f)
+    # separate sentences
+    sentences = []
+    sentence = []
+    for word in words:
+        if word == '.':
+            sentences.append(sentence)
+            sentence = []
+        else:
+            sentence.append(word)
+
+    # separate vertexSet, and add pos[start, end], sent_id, type to each vertex
+    vertexSet = []
+    for i, sentence in enumerate(sentences):
+        # tag the sentence
+        tagged_sentence = pos_tag(sentence)
+        for j, (word, tag) in enumerate(tagged_sentence):
+            # find pos end
+            if j == 0:
+                pos = [0, len(word)]
+            else:
+                pos = [vertexSet[-1]['pos'][1], vertexSet[-1]['pos'][1] + len(word)]
+
+            # Check if the tag is in ner2id
+            if tag in ner2id:
+                type_ = tag
+            else:
+                type_ = 'BLANK'  # use a default type
+
+            vertex = {
+                'name': word,
+                'pos': pos,
+                'sent_id': i,
+                'type': type_
+            }
+            vertexSet.append(vertex)
+
+    data = {
+        'sents': sentences,
+        'title': title,
+        'vertexSet': [vertexSet]
+    }
+
+    with open(output_file, 'a+') as f:
+        json.dump([data], f)
 
 
-def data_preprocess(text, device='mps'):
+def data_preprocess(text, title, output_file='./data/test_predict.json', device='mps'):
     # tokenize data
-    tokenize_data(text, '.data/test_predict.json')
[…]

### 2024-03-07 models/BERT.py

@@ -28,14 +28,6 @@ class BERT(nn.Module):
         self.use_coreference = True
         self.use_distance = True
 
-        # performance is similar with char_embed
-        # self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
-        # self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
-
-        # char_dim = config.data_char_vec.shape[1]
-        # char_hidden = 100
-        # self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
-
         hidden_size = 128
         #hidden_size = 768
         bert_hidden_size = 768
@@ -57,7 +49,6 @@ class BERT(nn.Module):
         #self.sent_rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
         #self.att_enc = SimpleEncoder(input_size, 4, 1)
         self.bert = BertModel.from_pretrained('bert-base-uncased')
-        #self.linear_re = nn.Linear(bert_hidden_size+config.coref_size+config.entity_type_size, hidden_size)
         self.linear_re = nn.Linear(bert_hidden_size, hidden_size)
         #self.ent_att_enc = SimpleEncoder(hidden_size*2, 4, 1)
 
@@ -81,32 +72,6 @@ class BERT(nn.Module):
 
     def forward(self, context_idxs, pos, context_ner, context_char_idxs, context_lens, h_mapping, t_mapping,
                 relation_mask, dis_h_2_t, dis_t_2_h, sent_idxs, sent_lengths, reverse_sent_idxs, context_masks, context_starts):
-        # para_size, char_size, bsz = context_idxs.size(1), context_char_idxs.size(2), context_idxs.size(0)
-        # context_ch = self.char_emb(context_char_idxs.contiguous().view(-1, char_size)).view(bsz * para_size, char_size, -1)
-        # context_ch = self.char_cnn(context_ch.permute(0, 2, 1).contiguous()).max(dim=-1)[0].view(bsz, para_size, -1)
-
-        '''
-        sent = self.word_emb(context_idxs)
-        if self.use_coreference:
-            sent = torch.cat([sent, self.entity_embed(pos)], dim=-1)
-
-        if self.use_entity_type:
-            sent = torch.cat([sent, self.ner_emb(context_ner)], dim=-1)
-
[…]

### 2024-03-07 models/LSTM.py

@@ -185,6 +185,8 @@ class EncoderLSTM(nn.Module):
         outputs = []
         if input_lengths is not None:
             lens = input_lengths.data.cpu().numpy()
+            # sort lens in decreasing order
+            lens = np.flip(np.sort(lens), axis=0).copy()
 
         for i in range(self.nlayers):
             hidden, c = self.get_init(bsz, i)

### 2024-03-07 test/__init__.py

@@ -1,0 +1,2 @@
+from .test import test
+from .test_predict import predict

### 2024-03-07 test/test.py

@@ -18,7 +18,7 @@ import torch
 def test(model_name='BERT', device='mps'):
     parser = argparse.ArgumentParser()
     parser.add_argument('--model_name', type = str, default = model_name, help = 'name of the model')
-    parser.add_argument('--save_name', type = str)
+    parser.add_argument('--save_name', type = str, default=model_name)
 
     parser.add_argument('--train_prefix', type = str, default = 'train')
     parser.add_argument('--test_prefix', type = str, default = 'dev_dev')
@@ -39,5 +39,5 @@ def test(model_name='BERT', device='mps'):
     #con.load_train_data()
     con.load_test_data()
     # con.set_train_model()
-    pretrain_model_name = 'checkpoint_' + model_name + '_bert_relation_exist_cls'
+    pretrain_model_name = model_name
     con.testall(model[args.model_name], args.save_name, args.input_theta, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)

### 2024-03-07 test/test_predict.py

@@ -18,7 +18,7 @@ import torch
 def predict(model_name='BERT', device='mps'):
     parser = argparse.ArgumentParser()
     parser.add_argument('--model_name', type = str, default = model_name, help = 'name of the model')
-    parser.add_argument('--save_name', type = str)
+    parser.add_argument('--save_name', type = str, default=model_name)
 
     parser.add_argument('--train_prefix', type = str, default = 'train')
     parser.add_argument('--test_prefix', type = str, default = 'dev_test_predict')
@@ -39,5 +39,5 @@ def predict(model_name='BERT', device='mps'):
     #con.load_train_data()
     con.load_predict_data()
     # con.set_train_model()
-    pretrain_model_name = 'checkpoint_' + model_name + '_bert_relation_exist_cls'
+    pretrain_model_name = model_name
     con.test_predect(model[args.model_name], args.save_name, args.input_theta, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)

### 2024-03-07 main.py
fixed some issues

@@ -83,7 +83,7 @@ def data_preprocess(text, title, output_file='./data/test_predict.json', device=
 
 def main():
     parser = argparse.ArgumentParser()
-    parser.add_argument('--run_type', type=str, default='predict')
+    parser.add_argument('--run_type', type=str, default='test')
     parser.add_argument('--model_name', type=str, default='LSTM')
     parser.add_argument('--need_generate_data', type=bool, default=False)
     parser.add_argument('--device', type=str, default='mps')

### 2024-03-07 models/LSTM.py

@@ -12,305 +12,234 @@ from torch.nn.utils import rnn
 
 
 class LSTM(nn.Module):
-    def __init__(self, config):
-        super(LSTM, self).__init__()
-        self.config = config
+	def __init__(self, config):
+		super(LSTM, self).__init__()
+		self.config = config
 
-        word_vec_size = config.data_word_vec.shape[0]
-        self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
-        self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
-        self.word_emb.weight.requires_grad = False
+		word_vec_size = config.data_word_vec.shape[0]
+		self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
+		self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
+		self.word_emb.weight.requires_grad = False
 
-        # self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
-        # self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
-        # char_dim = config.data_char_vec.shape[1]
-        # char_hidden = 100
-        # self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
-        self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
-        self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
+		# self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
+		# self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
+		# char_dim = config.data_char_vec.shape[1]
+		# char_hidden = 100
+		# self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
+		self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
+		self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
 
-        input_size = config.data_word_vec.shape[1] + config.coref_size + config.entity_type_size #+ char_hidden
-        hidden_size = 128
+		input_size = config.data_word_vec.shape[1] + config.coref_size + config.entity_type_size #+ char_hidden
+		hidden_size = 128
 
-        self.vae = VAE(Encoder(input_size, hidden_size, 500), Decoder(500, hidden_size, input_size))
[…]

### 2024-03-07 models/LSTM_updated.py

@@ -1,0 +1,316 @@
+import torch
+import torch.autograd as autograd
+import torch.nn as nn
+import torch.nn.functional as F
+import torch.optim as optim
+from torch.autograd import Variable
+from torch import nn
+import numpy as np
+import math
+from torch.nn import init
+from torch.nn.utils import rnn
+
+
+class LSTM_UP(nn.Module):
+    def __init__(self, config):
+        super(LSTM, self).__init__()
+        self.config = config
+
+        word_vec_size = config.data_word_vec.shape[0]
+        self.word_emb = nn.Embedding(word_vec_size, config.data_word_vec.shape[1])
+        self.word_emb.weight.data.copy_(torch.from_numpy(config.data_word_vec))
+        self.word_emb.weight.requires_grad = False
+
+        # self.char_emb = nn.Embedding(config.data_char_vec.shape[0], config.data_char_vec.shape[1])
+        # self.char_emb.weight.data.copy_(torch.from_numpy(config.data_char_vec))
+        # char_dim = config.data_char_vec.shape[1]
+        # char_hidden = 100
+        # self.char_cnn = nn.Conv1d(char_dim,  char_hidden, 5)
+        self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
+        self.ner_emb = nn.Embedding(7, config.entity_type_size, padding_idx=0)
+
+        input_size = config.data_word_vec.shape[1] + config.coref_size + config.entity_type_size #+ char_hidden
+        hidden_size = 128
+
+        self.vae = VAE(Encoder(input_size, hidden_size, 500), Decoder(500, hidden_size, input_size))
+
+        self.rnn = EncoderLSTM(input_size, hidden_size, 1, True, False, 1 - config.keep_prob, False)
+        self.attention = BiAttention(hidden_size, 1 - config.keep_prob)
+        self.linear_re = nn.Linear(512, 128)  # *4 for 2layer
+
+        self.bili = torch.nn.Bilinear(hidden_size+config.dis_size, hidden_size+config.dis_size, config.relation_num)
+
+        self.dis_embed = nn.Embedding(20, config.dis_size, padding_idx=10)
+
+    def forward(self, context_idxs, pos, context_ner, context_char_idxs, context_lens, h_mapping, t_mapping,
+                relation_mask, dis_h_2_t, dis_t_2_h):
+        # para_size, char_size, bsz = context_idxs.size(1), context_char_idxs.size(2), context_idxs.size(0)
[…]

### 2024-03-07 models/__init__.py

@@ -1,3 +1,4 @@
+from .LSTM_updated import LSTM_UP
 from .LSTM import LSTM
 from .LSTM_SP import LSTM_SP
 from .BERT import BERT

### 2024-03-07 test/test.py

@@ -29,7 +29,8 @@ def test(model_name='BERT', device='mps'):
 
     args = parser.parse_args()
     model = {
-        'LSTM': models.LSTM,
+        'LSTM_UP': models.LSTM_UP,
+		'LSTM': models.LSTM,
         'BERT': models.BERT,
         'ContextAware': models.ContextAware,
     }

### 2024-03-07 test/test_predict.py

@@ -29,6 +29,7 @@ def predict(model_name='BERT', device='mps'):
 
     args = parser.parse_args()
     model = {
+        'LSTM_UP': models.LSTM_UP,
         'LSTM': models.LSTM,
         'BERT': models.BERT,
         'ContextAware': models.ContextAware,

### 2024-03-07 train.py

@@ -27,6 +27,7 @@ def train(model_name='BERT', device='mps'):
 
 	args = parser.parse_args()
 	model = {
+		'LSTM_UP': models.LSTM_UP,
 		'LSTM': models.LSTM,
 		'BERT': models.BERT,
 		'ContextAware': models.ContextAware,

### 2024-03-07 models/LSTM.py
fixed some issues

@@ -192,6 +192,8 @@ class EncoderLSTM(nn.Module):
 		outputs = []
 		if input_lengths is not None:
 			lens = input_lengths.data.cpu().numpy()
+			# sort lens in decreasing order
+			lens = np.flip(np.sort(lens), axis=0).copy()
 
 		for i in range(self.nlayers):
 			hidden, c = self.get_init(bsz, i)

### 2024-03-07 models/LSTM_updated.py

@@ -13,7 +13,7 @@ from torch.nn.utils import rnn
 
 class LSTM_UP(nn.Module):
     def __init__(self, config):
-        super(LSTM, self).__init__()
+        super(LSTM_UP, self).__init__()
         self.config = config
 
         word_vec_size = config.data_word_vec.shape[0]

### 2024-03-07 configs/Config.py
fixed some issues of predict

@@ -1052,7 +1052,7 @@ class Config(object):
         f1, auc, pr_x, pr_y = self.test(model, model_name, True, input_theta, two_phase, pretrain_model)
 
 
-    def test_predect(self, model_pattern, model_name, input_theta, two_phase=False, pretrain_model_name=None):
+    def test_predect(self, model_pattern, model_name, input_theta, output=False, two_phase=False, pretrain_model_name=None):
         pretrain_model = None
         if two_phase:
             pretrain_model = model_pattern(config=self)
@@ -1068,7 +1068,7 @@ class Config(object):
 
         data_idx = 0
         eval_start_time = time.time()
-        # test_result_ignore = []
+        test_result_ignore = []
         total_recall_ignore = 0
 
         test_result = []
@@ -1128,7 +1128,10 @@ class Config(object):
 
             predict_re = predict_re.data.cpu().numpy()
 
-            # compress predict result to label
+            print("predict_re: ", predict_re.shape)
+
+            is_rel_exist = is_rel_exist.cpu().numpy() if two_phase else None
+
             for i in range(len(labels)):
                 label = labels[i]
                 index = indexes[i]
@@ -1160,19 +1163,19 @@ class Config(object):
                                     if label[(h_idx, t_idx, r)] == True:
                                         intrain = True
 
+                                if not intrain:
+                                    test_result_ignore.append( ((h_idx, t_idx, r) in label, float(predict_re[i,j,r]),  titles[i], self.id2rel[r], index, h_idx, t_idx, r) )
+
                                 if two_phase:
                                     if is_rel_exist[i, j, 1] > is_rel_exist[i, j, 0]:
-                                        test_result.append(
-                                            ((h_idx, t_idx, r) in label, float(predict_re[i, j, r]), intrain, titles[i],
-                                             self.id2rel[r], index, h_idx, t_idx, r))
+                                        test_result.append(((h_idx, t_idx, r) in label, float(predict_re[i, j, r]),
+                                                            intrain, titles[i], self.id2rel[r], index, h_idx, t_idx, r))
                                     else:
-                                        test_result.append(
-                                            ((h_idx, t_idx, r) in label, -100.0, intrain, titles[i], self.id2rel[r],
-                                             index, h_idx, t_idx, r))
+                                        test_result.append(((h_idx, t_idx, r) in label, -100.0, intrain, titles[i],
[…]

### 2024-03-07 main.py

@@ -1,5 +1,6 @@
 import argparse
 import json
+import random
 
 from nltk import word_tokenize, PorterStemmer, download, pos_tag
 from nltk.corpus import stopwords
@@ -9,6 +10,14 @@ from configs import generate_test_predict
 from test import test, predict
 from train import train
 
+
+def tag_to_type(tag):
+    word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
+    if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
+        return random.choice(word_types)
+
+    else:
+        return 'BLANK'
 
 def tokenize_data(text, title, output_file):
     download('punkt')
@@ -42,34 +51,31 @@ def tokenize_data(text, title, output_file):
     for i, sentence in enumerate(sentences):
         # tag the sentence
         tagged_sentence = pos_tag(sentence)
+        vertexs = []
         for j, (word, tag) in enumerate(tagged_sentence):
             # find pos end
             if j == 0:
                 pos = [0, len(word)]
             else:
-                pos = [vertexSet[-1]['pos'][1], vertexSet[-1]['pos'][1] + len(word)]
+                pos = [vertexs[-1]['pos'][1], vertexs[-1]['pos'][1] + len(word)]
 
-            # Check if the tag is in ner2id
-            if tag in ner2id:
-                type_ = tag
-            else:
-                type_ = 'BLANK'  # use a default type
-
+            type_ = tag_to_type(tag)
             vertex = {
                 'name': word,
                 'pos': pos,
                 'sent_id': i,
                 'type': type_
             }
-            vertexSet.append(vertex)
+            vertexs.append(vertex)
+        vertexSet.append(vertexs)
 
     data = {
         'sents': sentences,
         'title': title,
-        'vertexSet': [vertexSet]
+        'vertexSet': vertexSet
     }
 
-    with open(output_file, 'a+') as f:
+    with open(output_file, 'w') as f:
         json.dump([data], f)
 
 
@@ -83,8 +89,8 @@ def data_preprocess(text, title, output_file='./data/test_predict.json', device=
 
 def main():
     parser = argparse.ArgumentParser()
-    parser.add_argument('--run_type', type=str, default='test')
-    parser.add_argument('--model_name', type=str, default='LSTM')
+    parser.add_argument('--run_type', type=str, default='predict')
+    parser.add_argument('--model_name', type=str, default='LSTM_UP')
[…]

### 2024-03-07 test/test_predict.py

@@ -41,4 +41,4 @@ def predict(model_name='BERT', device='mps'):
     con.load_predict_data()
     # con.set_train_model()
     pretrain_model_name = model_name
-    con.test_predect(model[args.model_name], args.save_name, args.input_theta, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)
+    con.test_predect(model[args.model_name], args.save_name, args.input_theta, True, args.two_phase, pretrain_model_name)#, args.ignore_input_theta)

### 2024-03-07 train.py

@@ -36,7 +36,7 @@ def train(model_name='BERT', device='mps'):
 	con = configs.Config(args)
 	con.device = torch.device(device)
 	con.set_max_epoch(100)
-	con.set_batch_size(24)
+	con.set_batch_size(8)
 	con.load_train_data()
 	con.load_test_data()
 	# con.set_train_model()

### 2024-03-07 main.py
update BERT

@@ -90,9 +90,9 @@ def data_preprocess(text, title, output_file='./data/test_predict.json', device=
 def main():
     parser = argparse.ArgumentParser()
     parser.add_argument('--run_type', type=str, default='predict')
-    parser.add_argument('--model_name', type=str, default='LSTM_UP')
+    parser.add_argument('--model_name', type=str, default='BERT')
     parser.add_argument('--need_generate_data', type=bool, default=False)
-    parser.add_argument('--device', type=str, default='mps')
+    parser.add_argument('--device', type=str, default='cuda:0')
 
     args = parser.parse_args()
     # if you want to generate data, run this line

### 2024-03-07 models/BERT.py

@@ -28,8 +28,11 @@ class BERT(nn.Module):
         self.use_coreference = True
         self.use_distance = True
 
-        hidden_size = 128
-        #hidden_size = 768
+        # hidden_size = 128
+
+        hidden_size = 768
+        self.self_attention = SelfAttention(hidden_size)
+
         bert_hidden_size = 768
         input_size = config.data_word_vec.shape[1]
         if self.use_entity_type:
@@ -38,33 +41,23 @@ class BERT(nn.Module):
 
         if self.use_coreference:
             input_size += config.coref_size
-            # self.coref_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
             self.entity_embed = nn.Embedding(config.max_length, config.coref_size, padding_idx=0)
 
-        # input_size += char_hidden
 
         self.input_size = input_size
-
-        #self.rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
-        #self.sent_rnn = EncoderLSTM(input_size, hidden_size, 1, True, True, 1 - config.keep_prob, False)
-        #self.att_enc = SimpleEncoder(input_size, 4, 1)
         self.bert = BertModel.from_pretrained('bert-base-uncased')
         self.linear_re = nn.Linear(bert_hidden_size, hidden_size)
-        #self.ent_att_enc = SimpleEncoder(hidden_size*2, 4, 1)
 
         if self.use_distance:
             self.dis_embed = nn.Embedding(20, config.dis_size, padding_idx=10)
             self.bili = torch.nn.Bilinear(hidden_size+config.dis_size, hidden_size+config.dis_size, config.relation_num)
-            #self.linear_re = nn.Linear((hidden_size+config.dis_size)*2, config.relation_num)
         else:
-            #self.linear_re = nn.Linear(hidden_size*2, config.relation_num)
             self.bili = torch.nn.Bilinear(hidden_size, hidden_size, config.relation_num)
 
     def mask_lengths(self, batch_size, doc_size, lengths):
         masks = torch.ones(batch_size, doc_size).cuda()
         index_matrix = torch.arange(0, doc_size).expand(batch_size, -1).cuda()
         index_matrix = index_matrix.long()
-        #doc_lengths = torch.tensor(lengths).view(-1,1)
         doc_lengths = lengths.view(-1, 1)
         doc_lengths_matrix = doc_lengths.expand(-1, doc_size)
         masks[torch.ge(index_matrix-doc_lengths_matrix, 0)] = 0
[…]

### 2024-03-07 main.py
update tag to type

@@ -1,6 +1,7 @@
 import argparse
 import json
 import random
+import spacy
 
 from nltk import word_tokenize, PorterStemmer, download, pos_tag
 from nltk.corpus import stopwords
@@ -10,14 +11,39 @@ from configs import generate_test_predict
 from test import test, predict
 from train import train
 
+nlp = spacy.load("en_core_web_sm")
 
-def tag_to_type(tag):
-    word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
-    if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
-        return random.choice(word_types)
+# def tag_to_type(word, sentences):
+#     word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
+#     if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
+#         return random.choice(word_types)
 
-    else:
-        return 'BLANK'
+#     else:
+#         return 'BLANK'
+def tag_to_type(word,sentences,tag):
+    # Process sentences with spaCy to identify entities
+    checked = False
+    docs = nlp(sentences)
+
+    for sent_id, sent in enumerate(docs.sents):
+        for ent in sent.ents:
+            if word == ent:
+                checked = True
+                return ent.label_
+            
+    if checked == False:
+        # Define a simplistic and hypothetical mapping from POS tag to a NER type
+        tag_to_entity_type = {
+            'NNP': 'PER',  # Assuming proper nouns as person names, which is a simplification
+            'NNPS': 'PER',  # Same assumption for plural proper nouns
+            'NN': 'MISC',  # Common nouns as miscellaneous
+            'NNS': 'MISC',  # Plural nouns also as miscellaneous
+            'CD': 'NUM',  # Cardinal numbers
+            # Add more mappings as needed, understanding the limitations of this approach
+        }
+        # Return the entity type if available, else return 'UNKNOWN'
+        return tag_to_entity_type.get(tag, 'BLANK')
+            
 
 def tokenize_data(text, title, output_file):
     download('punkt')
@@ -59,7 +85,7 @@ def tokenize_data(text, title, output_file):
             else:
                 pos = [vertexs[-1]['pos'][1], vertexs[-1]['pos'][1] + len(word)]
 
-            type_ = tag_to_type(tag)
+            type_ = tag_to_type(word,text,tag)
             vertex = {
                 'name': word,
                 'pos': pos,
[…]

### 2024-03-08 models/BERT.py
added more details of readme, requirement and gitignore

@@ -8,6 +8,8 @@ from torch import nn
 import numpy as np
 import math
 from torch.nn import init
+from transformers.models.ctrl.modeling_ctrl import MultiHeadAttention
+
 from models.attention import SimpleEncoder
 from torch.nn.utils import rnn
 from transformers import *

### 2024-03-08 main.py
fix some test sence

@@ -2,6 +2,7 @@ import argparse
 import json
 import random
 import spacy
+import sys
 
 from nltk import word_tokenize, PorterStemmer, download, pos_tag
 from nltk.corpus import stopwords
@@ -13,7 +14,7 @@ from train import train
 
 nlp = spacy.load("en_core_web_sm")
 
-# def tag_to_type(word, sentences):
+# # def tag_to_type(word, sentences):
 #     word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
 #     if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
 #         return random.choice(word_types)
@@ -27,22 +28,18 @@ def tag_to_type(word,sentences,tag):
 
     for sent_id, sent in enumerate(docs.sents):
         for ent in sent.ents:
-            if word == ent:
+            if word == ent and ent.label_ in ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]:
                 checked = True
                 return ent.label_
             
     if checked == False:
         # Define a simplistic and hypothetical mapping from POS tag to a NER type
-        tag_to_entity_type = {
-            'NNP': 'PER',  # Assuming proper nouns as person names, which is a simplification
-            'NNPS': 'PER',  # Same assumption for plural proper nouns
-            'NN': 'MISC',  # Common nouns as miscellaneous
-            'NNS': 'MISC',  # Plural nouns also as miscellaneous
-            'CD': 'NUM',  # Cardinal numbers
-            # Add more mappings as needed, understanding the limitations of this approach
-        }
-        # Return the entity type if available, else return 'UNKNOWN'
-        return tag_to_entity_type.get(tag, 'BLANK')
+        word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
+        if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
+            return random.choice(word_types)
+
+        else:
+            return 'BLANK'
             
 
 def tokenize_data(text, title, output_file):
@@ -66,12 +63,15 @@ def tokenize_data(text, title, output_file):
     sentences = []
     sentence = []
     for word in words:
-        if word == '.':
+        if word == '.'or word =='?'or word =='!':
             sentences.append(sentence)
             sentence = []
         else:
             sentence.append(word)
-
+    # new added 
+    if len(sentences)==0:
+        print("it is not a proper sentence!!!")
+        sys.exit(-1)
[…]

### 2024-03-08 spacy_data.py

@@ -1,0 +1,47 @@
+import spacy
+import json
+
+def tokenize_data_spacy(text, title, output_file):
+    # 加载spaCy的英文模型
+    nlp = spacy.load("en_core_web_sm")
+    
+    # 处理文本
+    doc = nlp(text)
+    
+    # 初始化数据结构
+    sentences = []
+    vertexSet = []
+
+    for sent in doc.sents:
+        sentence = [token.text for token in sent if not token.is_stop]  # 分词且去除停用词
+        sentences.append(sentence)
+        
+        vertexs = []
+        for ent in sent.ents:  # 遍历句子中的命名实体
+            vertex = {
+                'name': ent.text,
+                'pos': [ent.start_char, ent.end_char],  # 使用字符级别的位置
+                'sent_id': len(sentences) - 1,  # 当前句子的索引
+                'type': ent.label_  # 实体类型
+            }
+            vertexs.append(vertex)
+        if vertexs:
+            vertexSet.append(vertexs)
+    
+    # 构建数据结构
+    data = {
+        'title': title,
+        'sents': sentences,
+        'vertexSet': vertexSet
+    }
+    
+    # 保存为JSON文件
+    with open(output_file, 'w') as f:
+        json.dump(data, f, ensure_ascii=False, indent=4)
+
+# 示例文本和调用函数
+text = "odel Performance. Table 4 shows the experimental results under the supervised and weakly supervised settings, from which we have the following observations: (1) Models trained with human annotated data generally outperform their counter parts trained on distantly supervised data."
+title = "Example Document"
+output_file = "spacy_formatted_data.json"
+tokenize_data_spacy(text, title, output_file)
+print(f"Data has been formatted and saved to '{output_file}'.")

### 2024-03-08 main.py
fixed some issues of readme and main

@@ -1,7 +1,6 @@
 import argparse
 import json
 import random
-import spacy
 import sys
 
 from nltk import word_tokenize, PorterStemmer, download, pos_tag
@@ -12,34 +11,14 @@ from configs import generate_test_predict
 from test import test, predict
 from train import train
 
-nlp = spacy.load("en_core_web_sm")
 
-# # def tag_to_type(word, sentences):
-#     word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
-#     if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
-#         return random.choice(word_types)
+def tag_to_type(tag):
+    word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
+    if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
+        return random.choice(word_types)
 
-#     else:
-#         return 'BLANK'
-def tag_to_type(word,sentences,tag):
-    # Process sentences with spaCy to identify entities
-    checked = False
-    docs = nlp(sentences)
-
-    for sent_id, sent in enumerate(docs.sents):
-        for ent in sent.ents:
-            if word == ent and ent.label_ in ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]:
-                checked = True
-                return ent.label_
-            
-    if checked == False:
-        # Define a simplistic and hypothetical mapping from POS tag to a NER type
-        word_types = ["ORG", "LOC", "TIME", "PER", "MISC", "NUM"]
-        if tag in ['NN', 'NNS', 'NNP', 'NNPS']:
-            return random.choice(word_types)
-
-        else:
-            return 'BLANK'
+    else:
+        return 'BLANK'
             
 
 def tokenize_data(text, title, output_file):
@@ -85,7 +64,7 @@ def tokenize_data(text, title, output_file):
             else:
                 pos = [vertexs[-1]['pos'][1], vertexs[-1]['pos'][1] + len(word)]
 
-            type_ = tag_to_type(word,text,tag)
+            type_ = tag_to_type(tag)
             vertex = {
                 'name': word,
                 'pos': pos,
@@ -116,9 +95,9 @@ def data_preprocess(text, title, output_file='./data/test_predict.json', device=
 def main():
     parser = argparse.ArgumentParser()
     parser.add_argument('--run_type', type=str, default='predict')
-    parser.add_argument('--model_name', type=str, default='LSTM')
[…]

### 2024-03-08 spacy_data.py

@@ -1,47 +1,0 @@
-import spacy
-import json
-
-def tokenize_data_spacy(text, title, output_file):
-    # 加载spaCy的英文模型
-    nlp = spacy.load("en_core_web_sm")
-    
-    # 处理文本
-    doc = nlp(text)
-    
-    # 初始化数据结构
-    sentences = []
-    vertexSet = []
-
-    for sent in doc.sents:
-        sentence = [token.text for token in sent if not token.is_stop]  # 分词且去除停用词
-        sentences.append(sentence)
-        
-        vertexs = []
-        for ent in sent.ents:  # 遍历句子中的命名实体
-            vertex = {
-                'name': ent.text,
-                'pos': [ent.start_char, ent.end_char],  # 使用字符级别的位置
-                'sent_id': len(sentences) - 1,  # 当前句子的索引
-                'type': ent.label_  # 实体类型
-            }
-            vertexs.append(vertex)
-        if vertexs:
-            vertexSet.append(vertexs)
-    
-    # 构建数据结构
-    data = {
-        'title': title,
-        'sents': sentences,
-        'vertexSet': vertexSet
-    }
-    
-    # 保存为JSON文件
-    with open(output_file, 'w') as f:
-        json.dump(data, f, ensure_ascii=False, indent=4)
-
-# 示例文本和调用函数
-text = "odel Performance. Table 4 shows the experimental results under the supervised and weakly supervised settings, from which we have the following observations: (1) Models trained with human annotated data generally outperform their counter parts trained on distantly supervised data."
-title = "Example Document"
-output_file = "spacy_formatted_data.json"
-tokenize_data_spacy(text, title, output_file)
-print(f"Data has been formatted and saved to '{output_file}'.")

### 2024-03-08 paper/paper.tex
update the paper

@@
 \usepackage{textcomp}
+\usepackage{float}
 \usepackage{xcolor}
 \usepackage{hyperref}
+\usepackage{booktabs}
 
@@
 
-\title{Text-Mining Short Paper}
+\title{Relation Extraction on DocRED: LSTM and BERT}
 \author{
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Document-level Relation Extraction is a task that poses unique challenges to traditional text mining techniques.
+DocRED is a dataset specifically created as grounds for experimentation with long-range Relation Extraction approaches \cite{yao2019docred}.
+Recent years have seen a focus on deep learning models for document-level Relation Extraction.
+This paper describes the development of two approaches: UP-LSTM, a model with no transformer; and UP-BERT, a model that makes use of transformers.
+Additions to the base concepts include variational auto-encoders and attention layers.
+These models were evaluated against each other and state-of-the-art benchmarks using the F1-Score, a harmonic mean between the precision and recall.
+Results show the effect of the adaptions made to the LSTM and BERT models, as well as the limitations of the approaches.
+
 \end{abstract}
-
-\begin{IEEEkeywords}
-component, formatting, style, styling, insert
-\end{IEEEkeywords}
 
@@
 
-DocRed dataset\cite{yao2019docred}
+Relation Extraction (RE) is the task of identifying and categorising semantic relationships between two named entities in a given piece of text.
+Generally, RE tasks focus on capturing relations between entities in the same sentence.
+The drawback of this approach is the lack of consideration for relations spanning across multiple sentences which are commonly found in natural language.
+DocRED is an RE dataset with human-annotated document-level relations\cite{yao2019docred} that aims to address this limitation presented by traditional RE models.
+According to the DocRED corpus sampled from Wikipedia documents, 40.7\% of relations happen across multiple sentences \cite{yao2019docred}, highlighting the importance of document-level RE datasets and research.
+With 132,375 entities and 56,354 relational facts \cite{yao2019docred}, DocRED has created a vast array of opportunities for different approaches tackling long-range RE.
+This paper outlines the development and evaluation of two such approaches, with a focus on their differing performances.
+Their fundamental ideas are built upon existing research, with several additions and alterations made for ensuring novelty and providing room for comparisons.
 
-\section{Literature Review}
+\section{Related Works}
 % (2) review previously reported work that is related to your approaches;
 
-DocRed dataset with LSTM\cite{yao2019docred}
+Traditional RE techniques such as symbolic or unsupervised approaches proved to be ineffective at capturing the long-range relations featured in DocRED, leading to experimentation with deep learning-based approaches.
+Initial work on DocRED used three deep-learning models that do not make use of transformers: a Convolutional Neural Network (CNN) based model, a Long Short-Term Memory (LSTM) based model, and a bidirectional LSTM based model (BiLSTM) \cite{yao2019docred}.
+The LSTM is a Recurrent Neural Network (RNN) which makes use of memory units to accumulate contextual patterns in sequences over a long distance without the risk of vanishing gradients \cite{cai2016bidirectional}.
+This approach mirrors the nature of document-level RE, with the relational information for entities scattered across multiple sentences.
+The RE models' performances were evaluated using the F1-Score and Area Under Curve (AUC) metrics.
+The results suggested that, out of the three models, the bidirectional LSTM was the most fit for document-level RE, consistently achieving the highest F1 and AUC scores, whilst the CNN performed the worst \cite{yao2019docred}.
+However, the paper also concluded that the benchmark models lagged behind human performance, emphasising the room for improvement in the field of study.
+One of the two approaches detailed in this paper builds upon the LSTM model with additional layers.
 
-CNN\cite{yao2019docred}
+Subsequent works introduced the notion of transformer-based deep learning models using BERT (Bidirectional Encoder Representations from Transformers) \cite{han2020novel}.
+BERT is a pre-trained and fine-tuned predictive model widely used in NLP tasks that transforms the text into a contextual encoding and facilitates document-level RE, as demonstrated by an increase in F1-Score from previous approaches \cite{devlin2018bert}\cite{han2020novel}.
+A plethora of additions and modifications have since been made to the basic BERT algorithm, constituting the state-of-the art benchmarks for document-level RE using the DocRED dataset.
+One such modification is the SAIS (Supervising and Augmenting Intermediate Steps) approach which explicitly supervises BERT to enhance its capability of capturing textual contexts and entity types rather than relying on the purely predictive nature of the model \cite{xiao2021sais}.
+Other modifications considered for the BERT model include the addition of Graph Aggregation-and Inference Networks (GAIN) which uses graph structures to model the relations between entities \cite{zeng2020double} and hybrid approaches which use a two-step process for fine-tuning BERT with a bidirectional LSTM, improving the entity relation prediction and increasing the F1-Score \cite{wang2019fine}.
+The second approach which will be discussed in this paper is a transformer-based BERT model.
 
-BiLSTM\cite{yao2019docred}
-
-SAIS-BERT\cite{xiao2021sais}
-
-GAIN-BERT\cite{zeng2020double}
-
-Two-steps BERT\cite{wang2019fine}
-
-DREEAM\cite{ma2023dreeam}
-
-SSAN-RoBERTa-large+Adaptation\cite{xu2021entity}
-
-KD-Rb-l\cite{tan2022document}
+Attention-based mechanisms are a type of enhancement to document-level RE approaches that have been successfully improving the F1-Score of models.
+Attention works by assigning a weight to each entity in the document based on the probability of a relation with the target entity, enabling RE regardless of the distance between entities \cite{vaswani2017attention}.
+The leading benchmark for RE in the DocRED dataset, DREEAM, makes use of evidence guided attention modules to further increase the F1-Score \cite{ma2023dreeam}.
+Other document-level RE works that have made use of attention layers are SSAN, which incorporates distinctive dependencies between pairs of entities into the attention modules \cite{xu2021entity} and KD-Rb-l, which makes use of knowledge distillation, adaptive focal loss, and axial attention \cite{tan2022document}.
+An added benefit of attention is the parallelisation of the predictive weights in a Transformer-based model, greatly reducing the runtime of training the model \cite{vaswani2017attention}.
+Attention was used as an enhancement for both the LSTM and the BERT-based approaches.
 
@@
 
-Two RE approaches: LSTM\cite{yao2019docred} updated with VAE layer and attention layer, and BERT\cite{zeng2020double} updated with ...
+There are two approaches improved upon in this paper, which are based on LSTM\cite{yao2019docred} and BERT\cite{wang2019fine} respectively.
+With consideration to the limitation of LSTM on DocRED dataset, this paper proposes an UP-LSTM method to use for RE on DocRED.
+Firstly, we add a variational auto-encoder (VAE) layer before the LSTM model, which could effectively extract features from data in unsupervised conditions via the embedding of data into latent dimension, which is then embedded back.
+Secondly, the attention layer is added after the LSTM model and before the output, with the goal of improving the handling of long dependencies and increasing the flexibility and efficiency of the model.
+Finally, during a series of experiments, this paper fine-tunes the model's hyper-parameters via the cross-validation method.
+
+Integrating a VAE and attention mechanisms into an LSTM framework for text mining can offer a unique set of advantages by combining the strengths of these distinct approaches.
+This integration can lead to models that are capable of generating more diverse, complex, and contextually relevant textual data, as well as providing improved performance on a range of text mining tasks.
+VAE learns compact and efficient representations of the input data in a latent space.
+Integrating a VAE with an LSTM allows the LSTM to leverage these representations to better capture the underlying structure and variability in the textual data.
+This can be particularly beneficial for tasks requiring an understanding of complex patterns in the data, such as text summarising or content generation.
+Moreover, in many text mining tasks, there is often more than one correct way to interpret or respond to a given piece of text.
+The combination of VAE, which can model variability and ambiguity in the data, with the context-aware processing of attention-enhanced LSTM allows for more nuanced and varied responses to textual inputs.
+
+Attention mechanisms enable the model to dynamically focus on different parts of an input sequence, which is crucial for tasks that require understanding the relevance of different words or phrases within a context.
+Besides, one of the key advantages of LSTM is the ability to capture long-term dependencies in sequence data.
+However, traditional LSTM may still struggle with very long sequences or when the relevant information is spread out across the sequence.
+Attention mechanisms can help the model to focus on the most relevant parts of the input sequence for making predictions, thereby enhancing its ability to deal with long-range dependencies.
+
+For the improvement of BERT, Zeng et al.
+proposed the use of a simple uncased BERT model to deal with the RE problem.
+This achieves better results than traditional methods on the DocRED dataset, such as CNNs, LSTM, and BiLSTM\cite{wang2019fine},  suggesting that the BERT method is a good fit for RE tasks in text mining.
+Based on their work, this paper proposes UP-BERT as an improvement to the classic BERT approach on the DocRED dataset.
+Compared to the classic BERT method, UP-BERT is updated with a dynamic variable for adjusting the learning rate during training and has been well-documented across a wide range of NLP tasks, leading to more efficient training and better model performance.
+In addition, to contribute to the model's ability to understand complex, nuanced language and to adapt to a wide range of tasks with remarkable effectiveness, a multi-head attention mechanism is added, which succeeds across numerous text mining and natural language processing applications.
+Furthermore, UP-BERT can be configured using entity types and can reference sizes dynamically, namely dynamic embedding size.
+Similar to UP-LSTM, hyper-parameter optimisation is performed using cross-validation.
+
+Implementing a dynamic learning rate can lead to improved model performance on various text mining tasks.
+By fine-tuning the learning rate, the model can better navigate the loss landscape, potentially avoiding local minima and making more efficient progress towards the global minimum.
+This can result in higher accuracy, better generalization, and improved performance on tasks such as sentiment analysis, document classification, and question answering.
+Meanwhile, a carefully scheduled learning rate can help prevent over-fitting, especially in the later stages of training.
+By reducing the learning rate over time, the model makes smaller adjustments to the weights, which can prevent it from fitting too closely to the training data and thus maintain its ability to generalize well to unseen data.
+
+The BERT model, as proposed by Google in 2018, leverages the Transformer architecture, which relies heavily on multi-head attention mechanisms to process and understand textual data\cite{elsahar2018t}.
+Therefore, multi-head attention allows BERT to capture a richer and more nuanced understanding of word context.
+By processing inputs through multiple attention heads, BERT can consider various aspects of each word in relation to the rest of the sentence.
+This enables the model to better understand the different meanings a word can have depending on its context, which is crucial for many text mining tasks.
+Moreover, by incorporating multiple attention heads, BERT can simultaneously learn to focus on different types of relationships between words, such as syntactic and semantic relationships.
+
+ Therefore, this paper tries to implement UP-LSTM and UP-BERT follow these structure.
+Meanwhile, for comparing with previous work more carefully and conveniently, we choose training epoch as 100 which is minimum but popular in previous work on DocRED dataset.
 
@@
 % here we should find out the popular evaluations in previous papers, such as precision, accuracy or F1 score. 
-Previous papers all use F1 score to evaluate the methods work on relation extraction (RE).
+When evaluating the performance of Relation Extraction (RE) models on the DocRED dataset, understanding the characteristics of different evaluation metrics is crucial. \cite{WangHong2019FBfD}
+Precision is an evaluation metric used to assess the performance of models, particularly in classification tasks.
+It measures the accuracy of the model in predicting positive instances (such as the existence of a relation) out of all instances it predicts as positive.
+In simpler terms, it's an indicator of how accurate the model is in predicting positive cases.\cite{alma992984185801101631}
+
+In formulaic terms, Precision is defined as:
+\[\text{Precision} = \frac{\text{True Positives (TP)}}{\text{True Positives (TP)} + \text{False Positives (FP)}}\]
+True Positives (TP): The number of instances correctly predicted as positive by the model.
+False Positives (FP): The number of instances incorrectly predicted as positive by the model.
+
+Recall is a metric used to evaluate the performance of classification models.
+It measures the proportion of actual positive instances (such as real relationships that exist) correctly identified by the model out of all actual positives.
+In simple terms, recall reflects the model's ability to capture true positive instances.\cite{alma992984185801101631}
+
+The formula for recall is: 
+\[\text{Recall} = \frac{\text{True Positives (TP)}}{\text{True Positives (TP)} + \text{False Negatives (FN)}}\]
+
+True Positives (TP): The number of instances that are correctly predicted as positive by the model.
+False Negatives (FN): The number of positive instances that the model incorrectly failed to identify.
+
+Accuracy is a commonly used metric for evaluating the performance of classification models.
+It measures the proportion of correct predictions (both positives and negatives) made by the model.
+In simple terms, accuracy reflects the overall correctness of the model's predictions across the entire dataset.\cite{alma992984185801101631}
+
+The formula for accuracy is:
+ \[\text{Accuracy} = \frac{\text{True Positives (TP)} + \text{True Negatives (TN)}}{\text{Total Number of Instances}}\]
+
+True Positives (TP): The number of instances correctly predicted as positive by the model.
+True Negatives (TN): The number of instances correctly predicted as negative by the model.
+Total Number of Instances: The total number of instances in the dataset.
+
+AUC-ROC is a crucial metric for evaluating the performance of classification models, assessing their capability to distinguish between positive and negative classes at various classification thresholds.
+The ROC curve is plotted by mapping the True Positive Rate (TPR) against the False Positive Rate (FPR), and the AUC-ROC value, which lies between 0 and 1, represents the area under this curve, with values closer to 1 indicating superior model performance.
+In contrast, AUC-PR focuses on performance in imbalanced datasets, evaluating the model based on the relationship between Precision and Recall.
+The PR curve is drawn using these two metrics, and the AUC-PR, the area under the PR curve, also ranges between 0 and 1, with higher values denoting better performance.
+Overall, both these metrics provide essential tools for assessing and comparing the performance of classification models, especially when dealing with various types of datasets.\cite{alma992984185801101631}
+
+The F1 score is a widely used metric for evaluating the performance of classification models, particularly suitable in situations where class distribution is imbalanced or when the costs of false positives and false negatives differ.\cite{alma992984185801101631}
+The F1 Score is defined as the harmonic mean of precision and recall. The formula for calculating the F1 score is:
+
+\[ \text{F1 Score} = 2 \times \frac{\text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}} \]
+
+Here, Precision is the ratio of true positive predictions to all positive predictions (including false positives), and Recall (or Sensitivity) is the ratio of true positive predictions to all actual positives (including false negatives).
+
+ The DocRED dataset aims to address the issue of relationships spanning across multiple sentences, which traditional Relation Extraction (RE) models do not consider.
+Given that document-level RE involves extracting relationships from multiple sentences, an evaluation metric needs to balance precision and recall.
+DocRED includes a variety of entities and relationships, which may present class imbalance issues.
+The F1 score offers a fairer performance evaluation in imbalanced datasets as it considers both false positives and false negatives.\cite{TanQingyu2022RD-A}
+ The F1 score, being the harmonic mean of precision and recall, can balance these two metrics.
+In document-level RE tasks, it's crucial not to sacrifice too much precision for recall, or vice versa.
+The F1 score provides a comprehensive assessment of model performance by combining precision and recall.
+This comprehensive evaluation is particularly important when assessing RE models that deal with complex relationships and contextual information.
+Previous research on the DocRED dataset often used the F1 score as the standard for evaluation, so employing the F1 score allows for better comparison and assessment against prior works.
 
 \section{Results}
+
+The result of our investigative endeavor is reflected in this section, where the experimental results highlight how well our improvements to the basic LSTM and BERT models worked.
+We give a comparison study after a thorough evaluation methodology that includes evaluations of the F1 score for both the BERT and UP-BERT models, as well as precision-recall (PR) curve assessments and the Area Under Curve (AUC) for the LSTM and UP-LSTM models.
+
+When compared to the original LSTM model, the revised UP-LSTM model's PR curve (Figure 2) shows some improvement in precision across almost all levels of recall.
+The curve remained more precise at lower recall thresholds, indicating that the UP-LSTM is lower accurate but more cautious when identifying positive connections.
+UP-LSTM performs not too bad, especially in the high-precision region along the y-axis, showing a smoother and less steep decrease.
+This suggests that the model can recover relevant relations with a low number of false positives.
+On the other hand, the precision fall in the PR curve of the original LSTM model (Figure 1) is greater, particularly in the middle range of recall levels.
+This shows that as recall increases, the original LSTM introduces more false positives even as it is able to detect more genuine positives.
+This is common for models that haven't been carefully adjusted or improved, where a recall gain frequently comes at a high cost to accuracy.
+
+\begin{figure}[H]
+    \centering
+    \begin{minipage}[t]{0.24\textwidth}
+        \centering
+        \includegraphics[width=4cm]{original.jpg}
+        \caption{LSTM}
+        \label{fig:lstm}
+    \end{minipage}
+    \begin{minipage}[t]{0.24\textwidth}
+         \centering
+         \includegraphics[width=4cm]{improved.jpg}
+         \caption{UP-LSTM}
+         \label{fig:up-lstm}
+    \end{minipage}
+    \begin{minipage}[t]{0.24\textwidth}
+        \centering
+        \includegraphics[width=4cm]{UP-BERT.png}
+        \caption{UP-BERT}
+        \label{fig:up-bert}
+    \end{minipage}
+\end{figure}
+
+The UP-LSTM model offers a better balance between precision and recall, as can be seen from the PR curves.
+The UP-LSTM model appears to have a higher area under the PR curve (AUC), supporting this theory.
+A higher AUC suggests that the model performs better overall and that UP-LSTM is more skilled at identifying real associations without being tricked by false positives.It's also critical to see how the curves behave as they approach the recall axis' ends.
+The model may have reached the point where it can no longer identify true positives without producing false positives, as evidenced by the original LSTM curve's more severe tailing-off.
+However, the more gradual tailing off of the UP-LSTM points to a stronger capacity for generalization and resilience across thresholding levels.
+
+\begin{table}[H]
+    \caption{\textbf{Metrices on Dev and Test dataset(\%)}}
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        &\multicolumn{2}{c}{\textbf{\underline{Dev}}}
+        &\multicolumn{2}{c}{\textbf{\underline{Test}}} \\
+        Model&F1&AUC&F1&AUC \\
+        \midrule
+        LSTM\cite{yao2019docred}&44.37&39.58&50.14&49.31 \\
+        LSTM (reappeared)&4.82&1.72&4.53&1.25 \\
+        UP-LSTM&5.08&1.44&4.46&1.15 \\
+        BERT\cite{zeng2020double}&54.16&50.13&53.25&49.56 \\
+        UP-BERT&27.58&18.65&21.00&10.86 \\ 
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{table}[H]
+    \caption{\textbf{Methods Comparison by F1-Score(\%)}}
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        Model&F1&Model&F1\\
+        \midrule
+        UP-LSTM&4.46&UP-BERT&21.00 \\
+        BiLSTM\cite{yao2019docred}&51.06&CNN\cite{yao2019docred}&42.33 \\
+        SAIS-BERT\cite{xiao2021sais}&62.77&GAIN\cite{zeng2020double}&62.76\\
+        SSAN\cite{xu2021entity}&58.16&DREEAM\cite{ma2023dreeam}&67.53 \\
+        KD-Rb-l\cite{TanQingyu2022RD-A}&67.28&& \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+Comparing F1-score (Table I) between original methods and updated methods on LSTM and BERT, it is clear that UP-BERT (27.58\%) illustrates approximately a 5 times increase than UP-LSTM (5.08\%) on dev dataset, and UP-LSTM shows higher F1-score than original LSTM (4.82\%) on dev dataset as well, but original LSTM (4.53\%) appears more effective than UP-LSTM (4.46\%) on test dataset.
+However, there is a big gap between LSTM and reappeared LSTM, UP-BERT and BERT, and UP-LSTM and LSTM.
+These may be related to insufficient training time, which need more experimentation to confirm.
+Furthermore, in Table II, comparing with other previous methods on DocRED dataset, BERT based methods (SAIS-62.77\%, SSAN-58.16\%) show better F1-score than other deep learning methods, such as BiLSTM (51.06\%), CNN (42.33\%) and GAIN (62.76\%).
+While, nowadays, DREEAM and KD-Rb-l as potential methods in the future show the highest score on the DocRED dataset: 67.53\% and 67.28\% respectively.
+
 % (5) discuss the results of your evaluation, comparing the approaches and highlighting their strengths and weaknesses.
+
+\section{Conclusion}
+
+From this study, there are some exposed limitations of UP-LSTM, LSTM, and UP-BERT, which would be valuable to tackle in the future.
+Firstly, during the experiment of reappearing LSTM methods, the F1 score results have a big gap with results from a previous paper, as well as UP-LSTM and UP-BERT.
+For this issue, more experiments on reappearing need to be done in the future.
+Secondly, via comparison of different methods results, BERT methods illustrate more potential effort on NLP problems.
+Therefore, in the future, we could implement more in this direction.
+Finally, in our research, DREEAM\cite{ma2023dreeam} and KD-Rb-l\cite{TanQingyu2022RD-A} methods with tweaks to the attention mechanisms show outstanding effort on RE of DocRED dataset.
+Pursuing this direction could lead to further improvement.
 
